---
title: "Matching Procedure - Entering Cruise Experiment"
description: |
  Comparing hours with entering cruise traffic to hours without. Adjusting for calendar and weather indicators.
author:
  - name: Marie-Abèle Bind 
    url: https://scholar.harvard.edu/marie-abele
    affiliation: Biostatistics Center, Massachusetts General Hospital
    affiliation_url: https://biostatistics.massgeneral.org/faculty/marie-abele-bind-phd/
  - name: Marion Leroutier 
    url: https://www.parisschoolofeconomics.eu/en/leroutier-marion/work-in-progress/
    affiliation: Misum, Stockholm School of Economics
    affiliation_url: https://www.hhs.se/en/persons/l/leroutier-marion/
  - name: Léo Zabrocki 
    url: https://lzabrocki.github.io/
    affiliation: Paris School of Economics
    affiliation_url: https://www.parisschoolofeconomics.eu/fr/zabrocki-leo/
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
      keep_md: true
      toc: true
      toc_depth: 2
---

<style>
body {
text-align: justify}
</style>

In this document, we provide all steps required to reproduce our matching procedure. We compare hours where:

* treated units are hours with positive entering cruise traffic in t.
* control units are hours without entering cruise traffic in t.

We adjust for calendar calendar indicator and weather confouding factors.

**Should you have any questions, need help to reproduce the analysis or find coding errors, please do not hesitate to contact us at leo.zabrocki@psemail.eu and marion.leroutier@psemail.eu.**

# Required Packages

To reproduce exactly the `1_script_matching_procedure.html` document, we first need to have installed:

* the [R](https://www.r-project.org/) programming language 
* [RStudio](https://rstudio.com/), an integrated development environment for R, which will allow you to knit the `1_script_matching_procedure.Rmd` file and interact with the R code chunks
* the [R Markdown](https://rmarkdown.rstudio.com/) package
* and the [Distill](https://rstudio.github.io/distill/) package which provides the template for this document. 

Once everything is set up, we have to load the following packages:

```{r, echo = TRUE, message = FALSE, warning = FALSE}
# load required packages
library(knitr) # for creating the R Markdown document
library(here) # for files paths organization
library(tidyverse) # for data manipulation and visualization
library(Rcpp) # for running the matching algorithm
library(optmatch) # for matching pairs
library(igraph) # for pair matching via bipartite maximal weighted matching
library(Cairo) # for printing customed police of graphs
```

We load the `script_time_series_matching_function.R` located in the *3.matching_analysis/0.script_matching_algorithm* folder and which provides the functions used for our matching procedure:

```{r, echo = TRUE, message = FALSE, warning = FALSE}
# command to overcome the Rcpp pakage error that forbids the compilation of the .Rmd file
Sys.setenv(PATH = "%PATH%;C:/Rtools/gcc-4.6.3/bin;c:/Rtools/bin")
# load matching functions
source(
  here::here(
    "2.scripts",
    "3.matching_analysis",
    "0.script_matching_algorithm",
    "script_time_series_matching_function.R"
  )
)
````

We use a custom `ggplot2` theme for graphs:

```{r, echo = TRUE, message = FALSE, warning = FALSE}
# load ggplot customed theme
source(
  here::here(
    "2.scripts",
    "4.custom_ggplot2_theme",
    "script_custom_ggplot_theme.R"
  )
)
````

The theme is based on the fantastic [hrbrthemes](https://hrbrmstr.github.io/hrbrthemes/index.html) package. If you do not want to use this theme or are unable to install it because of fonts issues, you can use the `theme_bw()` already included in the `ggplot2` package.

Finally, the matching procedure at the **hourly** level is computationally demanding and we could not run it on our local computer. Instead, we set up an RStudio version on Amazon Web Service EC2 and use a t3.2xlarge computer.

# Preparing the Data for Matching

### Selecting and Creating Relevant Variables

First, we load the data: 

```{r, echo=TRUE}
# load data
data_all_years <-
  readRDS(
    here::here(
      "1.data",
      "2.data_for_analysis",
      "0.main_data",
      "data_for_analysis_hourly.RDS"
    )
  )
````

Then, we select relevant variables for matching and create the **processed_data**:

```{r, echo=TRUE}
# select relevant variables
relevant_variables <- c(
  # date variable
  "date",
  # air pollutants variables
  "mean_no2_l",
  "mean_no2_sl",
  "mean_pm10_l",
  "mean_pm10_sl",
  "mean_pm25_l",
  "mean_so2_l",
  "mean_o3_l",
  # total gross tonnage
  "total_gross_tonnage",
  "total_gross_tonnage_entry",
  "total_gross_tonnage_exit",
  "total_gross_tonnage_other_vessels",
  "total_gross_tonnage_cruise",
  "total_gross_tonnage_ferry",
  "total_gross_tonnage_entry_cruise",
  "total_gross_tonnage_entry_ferry",
  "total_gross_tonnage_entry_other_vessels",
  "total_gross_tonnage_exit_cruise",
  "total_gross_tonnage_exit_ferry",
  "total_gross_tonnage_exit_other_vessels",
  # weather factors
  "temperature_average",
  "rainfall_height_dummy",
  "humidity_average",
  "wind_speed",
  "wind_direction_categories",
  "wind_direction_east_west",
  # road traffic variables
  "road_traffic_flow",
  # calendar data
  "hour",
  "day_index",
  "weekday",
  "holidays_dummy",
  "bank_day_dummy",
  "month",
  "year"
)

# create processed_data with the relevant variables
if (exists("relevant_variables") && !is.null(relevant_variables)) {
  # extract relevant variables (if specified)
  processed_data = data_all_years[relevant_variables]
} else {
  processed_data = data_all_years
}
````

For each covariate, we create the 0-3 hourly lags and leads:

```{r, echo=TRUE}
# we first define processed_data_leads and processed_data_lags
# to store leads and lags

processed_data_leads <- processed_data
processed_data_lags <- processed_data

#
# create leads
# 

# create a list to store dataframe of leads
leads_list <- vector(mode = "list", length = 3)
names(leads_list) <- c(1:3) 

# create the leads
for(i in 1:3){
  leads_list[[i]] <- processed_data_leads %>%
    mutate_at(vars(-date), ~  lead(., n = i, order_by = date)) %>%
    rename_at(vars(-date),function(x) paste0(x,"_lead_", i))
}

# merge the dataframes of leads
data_leads <- leads_list %>%
  reduce(left_join, by = "date")

# merge the leads with the processed_data_leads
processed_data_leads <- left_join(processed_data_leads, data_leads, by = "date") %>%
  select(-c(mean_no2_l:year))

#
# create lags
# 

# create a list to store dataframe of lags
lags_list <- vector(mode = "list", length = 3)
names(lags_list) <- c(1:3) 

# create the lags
for(i in 1:3){
  lags_list[[i]] <- processed_data_lags %>%
    mutate_at(vars(-date), ~  lag(., n = i, order_by = date)) %>%
    rename_at(vars(-date),function(x) paste0(x,"_lag_", i))
}

# merge the dataframes of lags
data_lags <- lags_list %>%
  reduce(left_join, by = "date")

# merge the lags with the initial processed_data_lags
processed_data_lags <- left_join(processed_data_lags, data_lags, by = "date")

#
# merge processed_data_leads with processed_data_lags
#

processed_data <- left_join(processed_data_lags, processed_data_leads, by = "date")
````

We can now define the hypothetical experiment that we would like to investigate.

### Defining the Hypothetical Experiment

We defined our potential experiments such that:* treated units are hours with positive entering cruise traffic in t.
* control units are hours without entering cruise traffic in t.

Below are the required steps to select the corresponding treated and control units whose observations are stored in the **
matching_data ** :

```{r, echo = TRUE}
# construct treatment assigment variable
processed_data <- processed_data %>%
mutate(is_treated = NA) %>%
# the hour is defined as treated if there was positive entering cruise traffic in t
mutate(is_treated = ifelse(total_gross_tonnage_entry_cruise > 0, TRUE, is_treated)) %>%
# the hour is defined as treated if there was no entering cruise traffic in t
mutate(is_treated = ifelse(total_gross_tonnage_entry_cruise == 0, FALSE, is_treated))

# remove the hours for which assignment is undefined
matching_data_all_years = processed_data[!is.na(processed_data$is_treated), ]

# susbet treated and control units
treated_units = subset(matching_data_all_years, is_treated)
control_units = subset(matching_data_all_years, !is_treated)
N_treated = nrow(treated_units) # gives the total number of treated units for all years
N_control = nrow(control_units) # gives the total number of control units for all years

# save matching_data_all_years
saveRDS(
matching_data_all_years,
here::here(
"1.data",
"2.data_for_analysis",
"1.matched_data",
"1.experiments_cruise",
"1.experiment_entry_cruise",
"matching_data.rds"
)
)
````

There are `r N_treated` treated units and  `r N_control` control units. 

# Matching Procedure

### Define Thresholds for Matching Covariates

Below is the code to define the relevant thresholds:

```{r, echo = TRUE}
# we create the scaling list as it is needed for running the algorithm
# but we do not use it

scaling =  rep(list(1),ncol(matching_data_all_years))
names(scaling) = colnames(matching_data_all_years)

# instead, we manually defined the threshold for each covariate
thresholds = rep(list(Inf),ncol(matching_data_all_years))
names(thresholds) = colnames(matching_data_all_years)

# threshold for hour
thresholds$hour = 0
thresholds$hour_lag_1 = 0
thresholds$hour_lag_2 = 0

# threshold for weekday
thresholds$weekday = 0
thresholds$weekday_lag_1 = 0
thresholds$weekday_lag_2 = 0

# threshold for holidays
thresholds$holidays_dummy = 0
thresholds$holidays_dummy_lag_1 = 0
thresholds$holidays_dummy_lag_2 = 0

# threshold for bank days
thresholds$bank_day_dummy = 0
thresholds$bank_day_dummy_lag_1 = 0
thresholds$bank_day_dummy_lag_2 = 0

# threshold for distance in days (day_index variable)
thresholds$day_index = 30

# thresholds for rainfall dummy
thresholds$rainfall_height_dummy = 0
thresholdsrainfall_height_dummy_lag_1 = 0
thresholds$rainfall_height_dummy_lag_2 = 0

# thresholds for average humidity
thresholds$humidity_average = 9
thresholds$humidity_average_lag_1 = 9
thresholds$humidity_average_lag_2 = 9

# thresholds for temperature average
thresholds$temperature_average = 4
thresholds$temperature_average_lag_1 = 4
thresholds$temperature_average_lag_2 = 4

# thresholds for wind direction categories
thresholds$wind_direction_east_west = 0
thresholds$wind_direction_east_west_lag_1 = 0
thresholds$wind_direction_east_west_lag_2 = 0

# thresholds for wind speed
thresholds$wind_speed = 1.8
thresholds$wind_speed_lag_1 = 1.8
thresholds$wind_speed_lag_2 =  1.8
````

### Running the Procedure

Once the thresholds values have been set, we can run the time series matching algorithm. Unfortunately, with `r nrow(matching_data_all_years)` observations, the matching procedure requires large computer power. We rented an Amazon Web Services virtual computer (EC2 t3.2xlarge) and even with this computation power, we had to run the matching on each year separetely. We proceeded as follows using a loop for each year:

* we loaded the data and prepare them for the matching procedure by defining treated and control units and setting up the thresholds values.
* we computed for each year the discrepancy matrix and ran the matching algorithm
* for somes cases, several controls units were matched to a treatment unit. We use the `igraph` package to force pair matching via bipartite maximal weighted matching.
* we saved each matched yearly file and merged them into a signle file with all years.

Below is the full code that we ran on the AWS EC2 t3.2xlarge computer:

```{r, echo = TRUE, eval = FALSE}
#--------------------------------------------------------------------

# SCRIPT: TIME SERIES MATCHING IN AWS FOR ENTERING CRUISE EXPERIMENT

#--------------------------------------------------------------------

# load required packages
library(tidyverse) # for data manipulation and visualization
library(Rcpp) # for running the matching algorithm
library(optmatch) # for matching pairs
library(igraph) # for pair matching via bipartite maximal weighted matching

# load matching functions
source("~/Dropbox/vessel_traffic_air_pollution_project/1.hourly_analysis/2.scripts/3.matching_analysis/0.script_matching_algorithm/script_time_series_matching_function.R")

# load data
data_all_years <- readRDS("~/Dropbox/vessel_traffic_air_pollution_project/1.hourly_analysis/1.data/2.data_for_analysis/0.main_data/data_for_analysis_hourly.RDS")

#-------------------------------------------------------------

# SETTING UP THE DATA FOR MATCHING

#-------------------------------------------------------------

# select relevant variables
relevant_variables <- c(
  # date variable
  "date", 
  # air pollutants variables
  "mean_no2_l", "mean_no2_sl", "mean_pm10_l", "mean_pm10_sl", "mean_pm25_l", "mean_so2_l", "mean_o3_l",
  # total gross tonnage
  "total_gross_tonnage", "total_gross_tonnage_entry", "total_gross_tonnage_exit",
  "total_gross_tonnage_other_vessels", "total_gross_tonnage_cruise", "total_gross_tonnage_ferry",
  "total_gross_tonnage_entry_cruise", "total_gross_tonnage_entry_ferry", "total_gross_tonnage_entry_other_vessels",
  "total_gross_tonnage_exit_cruise", "total_gross_tonnage_exit_ferry", "total_gross_tonnage_exit_other_vessels",
  # weather factors
  "temperature_average", "rainfall_height_dummy", "humidity_average", "wind_speed", "wind_direction_categories", "wind_direction_east_west",
  # road traffic flow
  "road_traffic_flow",
  # calendar data
  "hour", "day_index", "weekday", "holidays_dummy", "bank_day_dummy", "month", "year")

# create processed_data with the relevant variables
if (exists("relevant_variables") && !is.null(relevant_variables)){
  # extract relevant variables (if specified)
  processed_data = data_all_years[relevant_variables]
} else {
  processed_data = data_all_years
}


#-----------------------------------------------------------------------------------------------------------

# CREATING LAGS AND LEAGS 

#-----------------------------------------------------------------------------------------------------------

# we first define processed_data_leads and processed_data_lags
# to store leads and lags

processed_data_leads <- processed_data
processed_data_lags <- processed_data

#
# create leads
# 

# create a list to store dataframe of leads
leads_list <- vector(mode = "list", length = 3)
names(leads_list) <- c(1:3) 

# create the leads
for(i in 1:3){
  leads_list[[i]] <- processed_data_leads %>%
    mutate_at(vars(-date), ~  lead(., n = i, order_by = date)) %>%
    rename_at(vars(-date),function(x) paste0(x,"_lead_", i))
}

# merge the dataframes of leads
data_leads <- leads_list %>%
  reduce(left_join, by = "date")

# merge the leads with the processed_data_leads
processed_data_leads <- left_join(processed_data_leads, data_leads, by = "date") %>%
  select(-c(mean_no2_l:year))

#
# create lags
# 

# create a list to store dataframe of lags
lags_list <- vector(mode = "list", length = 3)
names(lags_list) <- c(1:3) 

# create the lags
for(i in 1:3){
  lags_list[[i]] <- processed_data_lags %>%
    mutate_at(vars(-date), ~  lag(., n = i, order_by = date)) %>%
    rename_at(vars(-date),function(x) paste0(x,"_lag_", i))
}

# merge the dataframes of lags
data_lags <- lags_list %>%
  reduce(left_join, by = "date")

# merge the lags with the initial processed_data_lags
processed_data_lags <- left_join(processed_data_lags, data_lags, by = "date")

#
# merge processed_data_leads with processed_data_lags
#

processed_data <- left_join(processed_data_lags, processed_data_leads, by = "date")

#-----------------------------------------------------------------------------

# DEFINING TREATMENT ASSIGNMENT

#-----------------------------------------------------------------------------

# construct treatment assigment variable
processed_data <- processed_data %>% 
  mutate(is_treated = NA) %>%
  # the hour is defined as treated if there was positive cruise traffic in t
  mutate(is_treated = ifelse(total_gross_tonnage_entry_cruise > 0, TRUE, is_treated)) %>% 
  # the hour is defined as treated if there was no cruise traffic in t
  mutate(is_treated = ifelse(total_gross_tonnage_entry_cruise == 0, FALSE, is_treated))

# remove the hours for which assignment is undefined
matching_data_all_years = processed_data[!is.na(processed_data$is_treated),]

# susbet treated and control units
treated_units = subset(matching_data_all_years,is_treated)
control_units = subset(matching_data_all_years,!is_treated)
N_treated = nrow(treated_units) # gives the total number of treated units for all years
N_control = nrow(control_units) # gives the total number of control units for all years

# save matching_data_all_years as matching_data
saveRDS(matching_data_all_years, "~/Dropbox/vessel_traffic_air_pollution_project/1.hourly_analysis/1.data/2.data_for_analysis/1.matched_data/1.experiments_cruise/1.experiment_entry_cruise/matching_data.rds.RDS")

#---------------------------------------------------------------------------

# DEFINING THRESHOLDS

#---------------------------------------------------------------------------

# we create the scaling list as it is needed for running the algorithm
# but we do not use it

scaling =  rep(list(1),ncol(matching_data_all_years))
names(scaling) = colnames(matching_data_all_years)

# instead, we manually defined the threshold for each covariate
thresholds = rep(list(Inf),ncol(matching_data_all_years))
names(thresholds) = colnames(matching_data_all_years)

# threshold for hour
thresholds$hour = 0
thresholds$hour_lag_1 = 0
thresholds$hour_lag_2 = 0

# threshold for weekday
thresholds$weekday = 0
thresholds$weekday_lag_1 = 0
thresholds$weekday_lag_2 = 0

# threshold for holidays
thresholds$holidays_dummy = 0
thresholds$holidays_dummy_lag_1 = 0
thresholds$holidays_dummy_lag_2 = 0

# threshold for bank days
thresholds$bank_day_dummy = 0
thresholds$bank_day_dummy_lag_1 = 0
thresholds$bank_day_dummy_lag_2 = 0

# threshold for distance in days (day_index variable)
thresholds$day_index = 30

# thresholds for rainfall dummy
thresholds$rainfall_height_dummy = 0
thresholdsrainfall_height_dummy_lag_1 = 0
thresholds$rainfall_height_dummy_lag_2 = 0

# thresholds for average humidity
thresholds$humidity_average = 9
thresholds$humidity_average_lag_1 = 9
thresholds$humidity_average_lag_2 = 9

# thresholds for temperature average
thresholds$temperature_average = 4
thresholds$temperature_average_lag_1 = 4
thresholds$temperature_average_lag_2 = 4

# thresholds for wind direction categories
thresholds$wind_direction_east_west = 0
thresholds$wind_direction_east_west_lag_1 = 0
thresholds$wind_direction_east_west_lag_2 = 0

# thresholds for wind speed
thresholds$wind_speed = 1.8
thresholds$wind_speed_lag_1 = 1.8
thresholds$wind_speed_lag_2 =  1.8

#--------------------------------------------------------------------------------

# RUNNING THE MATCHING PROCEDURE

#--------------------------------------------------------------------------------

# we run the matching procedure for each year on the amazon EC2 t3.2xlarge
# we cannot run the matching on the full dataset at once
# as the computation is too intensive

# running the loop

for (i in 2008:2018){
  # select relevant year
  matching_data <- matching_data_all_years %>%
    filter(year == i)
  
  # susbet treated and control units
  treated_units = subset(matching_data,is_treated)
  control_units = subset(matching_data,!is_treated)
  N_treated = nrow(treated_units)
  N_control = nrow(control_units)
  
  #-----------------------------------------------------------------------------------
  
  # COMPUTE DISCREPANCY MATRIX
  
  #-----------------------------------------------------------------------------------
  
  # first we compute the discrepancy matrix
  discrepancies = discrepancyMatrix(treated_units, control_units, thresholds, scaling)
  
  rownames(discrepancies) = format(matching_data$date[which(matching_data$is_treated)])
  colnames(discrepancies) = format(matching_data$date[which(!matching_data$is_treated)])
  rownames(matching_data) = matching_data$date
  
  #-----------------------------------------------------------------------------------
  
  # RUN MATCHING
  
  #-----------------------------------------------------------------------------------
  
  # run the fullmatch algorithm
  matched_groups = fullmatch(discrepancies, data = matching_data, remove.unmatchables = TRUE, max.controls = 1)
  
  # get list of matched  treated-control groups
  groups_labels = unique(matched_groups[!is.na(matched_groups)])
  groups_list = list()
  for (j in 1:length(groups_labels)){
    IDs = names(matched_groups)[(matched_groups==groups_labels[j])]
    groups_list[[j]] = as.Date(IDs[!is.na(IDs)])
  }
  
  #-----------------------------------------------------------------------------------
  
  # BIPARTITE GRAPH AND GET FINAL DATA
  
  #-----------------------------------------------------------------------------------
  
  # we build a bipartite graph with one layer of treated nodes, and another layer of control nodes.
  # the nodes are labeled by integers from 1 to (N_treated + N_control)
  # by convention, the first N_treated nodes correspond to the treated units, and the remaining N_control
  # nodes correspond to the control units.
  
  # build pseudo-adjacency matrix: edge if and only if match is admissible
  # NB: this matrix is rectangular so it is not per say the adjacendy matrix of the graph
  # (for this bipartite graph, the adjacency matrix had four blocks: the upper-left block of size
  # N_treated by N_treated filled with 0's, bottom-right block of size N_control by N_control filled with 0's,
  # top-right block of size N_treated by N_control corresponding to adj defined below, and bottom-left block
  # of size N_control by N_treated corresponding to the transpose of adj)
  adj = (discrepancies<Inf)
  
  # extract endpoints of edges
  edges_mat = which(adj,arr.ind = TRUE)
  
  # build weights, listed in the same order as the edges (we use a decreasing function x --> 1/(1+x) to
  # have weights inversely proportional to the discrepancies, since maximum.bipartite.matching
  # maximizes the total weight and we want to minimize the discrepancy)
  weights = 1/(1+sapply(1:nrow(edges_mat),function(j)discrepancies[edges_mat[j,1],edges_mat[j,2]]))
  
  # format list of edges (encoded as a vector resulting from concatenating the end points of each edge)
  # i.e c(edge1_endpoint1, edge1_endpoint2, edge2_endpoint1, edge2_endpoint1, edge3_endpoint1, etc...)
  edges_mat[,"col"] = edges_mat[,"col"] + N_treated
  edges_vector = c(t(edges_mat))
  
  # NB: by convention, the first N_treated nodes correspond to the treated units, and the remaining N_control
  # nodes correspond to the control units (hence the "+ N_treated" to shift the labels of the control nodes)
  
  # build the graph from the list of edges
  BG = make_bipartite_graph(c(rep(TRUE,N_treated),rep(FALSE,N_control)), edges = edges_vector)
  
  # find the maximal weighted matching
  MBM = maximum.bipartite.matching(BG,weights = weights)
  
  # list the dates of the matched pairs
  pairs_list = list()
  N_matched = 0
  for (j in 1:N_treated){
    if (!is.na(MBM$matching[j])){
      N_matched = N_matched + 1
      pairs_list[[N_matched]] = c(treated_units$date[j],control_units$date[MBM$matching[j]-N_treated])
    }
  }
  
  # transform the list of matched pairs to a dataframe
  matched_pairs <- enframe(pairs_list) %>%
    unnest(cols = "value") %>%
    rename(pair_number = name,
           date = value)
  
  # select the matched data for the analysis
  final_data <- left_join(matched_pairs, matching_data, by = "date")
  
  # save the data
  saveRDS(final_data, paste0(paste0("~/Dropbox/vessel_traffic_air_pollution_project/1.hourly_analysis/1.data/2.data_for_analysis/1.matched_data/1.experiments_cruise/1.experiment_entry_cruise/temporary_matched_data_", i), ".RDS"))
}

#-----------------------------------------------------------------------------------------------------------

# COMBINING YEARLY DATA INTO A SINGLE FILE

#-----------------------------------------------------------------------------------------------------------

# list the names of the matched data for each year
matched_data_all_years <- list.files(path = "~/Dropbox/vessel_traffic_air_pollution_project/1.hourly_analysis/1.data/2.data_for_analysis/1.matched_data/1.experiments_cruise/1.experiment_entry_cruise/",
                                     pattern = "temporary", 
                                     full.names = T) %>%
  map_df(~readRDS(.))

# recreate the pair ids
matched_data_all_years <- matched_data_all_years %>%
  mutate(pair_number = rep(1:(nrow(matched_data_all_years)/2), each=2))

# save the data
saveRDS(matched_data_all_years, "~/Dropbox/vessel_traffic_air_pollution_project/1.hourly_analysis/1.data/2.data_for_analysis/1.matched_data/1.experiments_cruise/1.experiment_entry_cruise/matched_data_entry_cruise.RDS")
```

# Matching Results

We open the matched data:

```{r, echo = TRUE}
matched_data <-
  readRDS(
    here::here(
      "1.data",
      "2.data_for_analysis",
      "1.matched_data",
      "1.experiments_cruise",
      "1.experiment_entry_cruise",
      "matched_data_entry_cruise.RDS"
    ))
```

The matching procedure resulted in `r nrow(matched_data)/2` matched pairs.


