---
title: " Exploratory Data Analysis"
description: |
  Daily level.
author:
  - name: Marie-Abèle Bind 
    url: https://scholar.harvard.edu/marie-abele
    affiliation: Harvard University
    affiliation_url: https://statistics.fas.harvard.edu/people/marie-abale-bind
  - name: Marion Leroutier 
    url: https://www.parisschoolofeconomics.eu/en/leroutier-marion/work-in-progress/
    affiliation: Paris School of Economics
    affiliation_url: https://www.parisschoolofeconomics.eu/en/
  - name: Léo Zabrocki 
    url: https://www.parisschoolofeconomics.eu/en/
    affiliation: Paris School of Economics
    affiliation_url: https://www.parisschoolofeconomics.eu/en/
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
      toc: true
      toc_depth: 2
---

<style>
body {
text-align: justify}
</style>

```{r setup, include=FALSE, results='hide', warning=FALSE}
library(knitr) # for creating the R Markdown document
opts_chunk$set(message = FALSE,
               warning = FALSE,
               out.width = "100%",
               dpi = 300)  
```

In this document, we carry out an exploratory data analysis at the daily level to better understand the distribution and the relationships among our variables. **Should you have any questions or find errors, please do not hesitate to reach us at leo.zabrocki@psemail.eu and marion.leroutier@psemail.eu**

# Required Packages and Data Loading

To reproduce exactly the `script_exploratory_data_analysis.html` document, we first need to have installed:

* the [R](https://www.r-project.org/) programming language on your computer 
* [RStudio](https://rstudio.com/), an integrated development environment for R, which will allow you to knit the `script_exploratory_data_analysis.Rmd` file and interact with the R code chunks
* the [R Markdown](https://rmarkdown.rstudio.com/) package
* and the [Distill](https://rstudio.github.io/distill/) package which provides the template of this document. 

Once everything is set up, we have to load the following packages:

```{r, echo=TRUE}
# load required packages
library(here) # for files paths organization
library(tidyverse) # for data manipulation and visualization
library(openair) # for polar plots of air pollutant concentrations
library(kableExtra) # for table formatting
library(Cairo) # for printing customed police of graphs
```

We load our custom `ggplot2` theme for graphs:

```{r, echo = TRUE}
# load ggplot customed theme
source(here("2.scripts", "5.custom_ggplot2_theme", "script_custom_ggplot_theme.R"))
````

The theme is based on the fantastic [hrbrthemes](https://hrbrmstr.github.io/hrbrthemes/index.html) package. If you do not want to use this theme or are unable to install it because of fonts issues, you can use the `theme_mimimal()` included in the `ggplot2` package.

Finally, we load the data: 

```{r, echo=TRUE}
# load data
data <- readRDS(here("1.data", "2.data_for_analysis", "0.main_data", "data_for_analysis_daily.RDS"))
````

# Maritime Traffic Data

We explore here the seasonal and long-run patterns of cruise traffic.

### Long-Term Evolution of Cruise Traffic

We plot the average daily gross tonnage of cruise traffic for each month over the 2008-2018 period:

```{R, echo=TRUE, layout="l-body-outset", fig.width=28, fig.height=15, dev = "CairoPNG"}
# cruise traffic - time series for all years at the monthly level
data_month <- data %>%
  mutate(month_year = lubridate::floor_date(date, "month")) %>%
  group_by(month_year) %>%
  summarise(mean_total_gross_tonnage_cruise = mean(total_gross_tonnage_cruise, na.rm = TRUE))

data_year <- data %>%
   group_by(year) %>%
  summarise(mean_total_gross_tonnage_cruise = mean(total_gross_tonnage_cruise, na.rm = TRUE))

# make the graph
ts_cruise_tonnage_evolution <- ggplot(data_month, aes(x = month_year, y = mean_total_gross_tonnage_cruise)) + geom_line(color = "deepskyblue3", size = 1.5) +
  scale_x_date(date_labels = "%m-%Y", breaks = scales::pretty_breaks(n = 10)) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5), labels = function(x) format(x, big.mark = " ", scientific = FALSE)) +  
  ylab("Monthly Average of Daily Gross Tonnage") +
  xlab("Date") +
  custom_theme

# print the graph
ts_cruise_tonnage_evolution

# save the graph
ggsave(ts_cruise_tonnage_evolution, filename = here("3.outputs", "1.figures", "1.eda", "ts_cruise_tonnage_evolution.pdf"), 
       width = 40, height = 20, units = "cm", device = cairo_pdf)
````

### Monthly Seasonality of Cruise Traffic

We plot the distribution of the daily gross tonnage of cruise traffic for each month:

```{R, echo=TRUE, layout="l-body-outset", fig.width=20, fig.height=10, dev = "CairoPNG"}
# distribution of cruise tonnage by month
graph_distribution_tonnage_month <- data %>%
  ggplot(., aes(x = total_gross_tonnage_cruise, y = reorder(month, desc(month)))) +
  geom_boxplot(colour = "deepskyblue3", size = 1.3) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 5), labels = function(x) format(x, big.mark = " ", scientific = FALSE)) +  
  xlab("Daily Gross Tonnage") + ylab("") +
  custom_theme +
  theme(
    axis.title.x = element_text(
      size = 40,
      face = "bold",
      margin = margin(
        t = 20,
        r = 0,
        b = 0,
        l = 0
      )
    ),
    axis.text.x = element_text(size = 26),
    axis.text.y = element_text(size = 26)
  )

# print the graph
graph_distribution_tonnage_month

# save the graph
ggsave(graph_distribution_tonnage_month, filename = here("3.outputs", "1.figures", "1.eda", "graph_distribution_tonnage_month.pdf"), 
       width = 50, height = 30, units = "cm", device = cairo_pdf)
````

### Weekly Variation of Cruise Traffic

We plot the distribution of the daily gross tonnage of cruise traffic for each day of the week:

```{R, echo=TRUE, layout="l-body-outset", fig.width=20, fig.height=10, dev = "CairoPNG"}
# density of tonnage by day of the week
graph_distribution_tonnage_weekday <- data %>%
  ggplot(., aes(x = total_gross_tonnage_cruise, y = reorder(weekday, desc(weekday)))) +
  geom_boxplot(colour = "deepskyblue3", size = 1.3) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 5), labels = function(x) format(x, big.mark = " ", scientific = FALSE)) +  
  xlab("Daily Gross Tonnage") + ylab("") +
  custom_theme +
  theme(
    axis.title.x = element_text(
      size = 40,
      face = "bold",
      margin = margin(
        t = 20,
        r = 0,
        b = 0,
        l = 0
      )
    ),
    axis.text.x = element_text(size = 26),
    axis.text.y = element_text(size = 26)
  )

# print the graph
graph_distribution_tonnage_weekday

# save the graph
ggsave(graph_distribution_tonnage_weekday, filename = here("3.outputs", "1.figures", "1.eda", "graph_distribution_tonnage_weekday.pdf"), 
       width = 50, height = 30, units = "cm", device = cairo_pdf)
````

# Air Pollutants

We explore here the seasonal and long-run patterns of air pollutant concentrations.

### Long-term Evolution of Air Pollutant Concentrations

We plot the daily average concentration of a pollutant for each month over the 2008-2018 period:

```{R, echo=TRUE, layout="l-body-outset", fig.width=54, fig.height=15, dev = "CairoPNG"}
# pollutant concentration - time series for all years at the month level
data_pollutant_month_year <- data %>%
  mutate(month_year = lubridate::floor_date(date, "month")) %>%
  group_by(month_year) %>%
  summarise_at(vars( mean_no2_sl,mean_no2_l, mean_pm10_sl, mean_pm10_l, mean_pm25_l, mean_so2_l, mean_o3_l), 
               ~ mean(., na.rm = TRUE)) %>%
  pivot_longer(cols = c(mean_no2_sl:mean_o3_l), names_to = "pollutant", values_to = "concentration")


# correctly label the variables
variable_labels <- c(mean_no2_sl = "NO2 Saint-Louis",
                     mean_no2_l = "NO2 Longchamp",
                     mean_pm10_sl = "PM10 Saint-Louis",
                     mean_pm10_l = "PM10 Longchamp",
                     mean_pm25_l = "PM2.5 Longchamp",
                     mean_so2_l = "SO2 Longchamp",
                     mean_o3_l = "O3 Longchamp")

data_pollutant_month_year$pollutant <- plyr::revalue(data_pollutant_month_year$pollutant, variable_labels)

# make the graph
ts_pollutant_evolution <- ggplot(data_pollutant_month_year, aes(x = month_year, y = concentration)) + 
  geom_line(color = "deepskyblue3", size = 1.4) +
  scale_x_date(date_labels = "%m-%Y", breaks = scales::pretty_breaks(n = 5)) +
  facet_wrap(~ pollutant, scales = "free", ncol = 4) +
  ylab("Concentration (µg/m³)") +
  xlab("Date") +
  custom_theme +
  theme(
    # axis titles parameters
    axis.title.x = element_text(size=40, face = "bold", margin = margin(t = 20, r = 0, b = 0, l =0)),
    axis.title.y = element_text(size=40, face = "bold", margin = margin(t = 0, r = 20, b = 0, l = 0)),
    # axis texts
    axis.text.x = element_text(size=20),
    axis.text.y = element_text(size=20),
    # facet texts
    strip.text.x = element_text(size=30, face = "bold"),
    strip.text.y = element_text(size=30, face = "bold"))

# print the graph
ts_pollutant_evolution

# save the graph
ggsave(ts_pollutant_evolution, filename = here("3.outputs", "1.figures", "1.eda", "ts_pollutant_evolution.pdf"), 
       width = 90, height = 30, units = "cm", device = cairo_pdf)
````

### Weekly Variation of Air Pollutant Concentrations

We plot the distribution of the daily average concentration of a pollutant for each day of the week:

```{R, echo=TRUE, layout="l-body-outset",  fig.width=45, fig.height=14, dev = "CairoPNG"}
# reshape data into long format
data_pollutant_weekday <- data %>%
  select(weekday, mean_no2_sl,mean_no2_l, mean_pm10_sl, mean_pm10_l, mean_pm25_l, mean_so2_l, mean_o3_l) %>%
  pivot_longer(cols = c(mean_no2_sl:mean_o3_l), names_to = "pollutant", values_to = "concentration")

# correctly label the variables
variable_labels <- c(mean_no2_sl = "NO2 Saint-Louis",
                     mean_no2_l = "NO2 Longchamp",
                     mean_pm10_sl = "PM10 Saint-Louis",
                     mean_pm10_l = "PM10 Longchamp",
                     mean_pm25_l = "PM2.5 Longchamp",
                     mean_so2_l = "SO2 Longchamp",
                     mean_o3_l = "O3 Longchamp")

data_pollutant_weekday$pollutant <- plyr::revalue(data_pollutant_weekday$pollutant, variable_labels)

# make the graph
graph_distribution_pollutant_weekday <- ggplot(data_pollutant_weekday, aes(x = weekday, y = concentration)) +  
  geom_boxplot(colour = "deepskyblue3", size = 1.4) + 
  facet_wrap(~ pollutant, scales = "free", ncol = 4) +
  xlab("") + ylab("Concentration (µg/m³)") +
  custom_theme +
  theme(
    # axis titles parameters
    axis.title.x = element_text(size=40, face = "bold", margin = margin(t = 20, r = 0, b = 0, l =0)),
    axis.title.y = element_text(size=40, face = "bold", margin = margin(t = 0, r = 20, b = 0, l = 0)),
    # axis texts
    axis.text.x = element_text(size=20),
    axis.text.y = element_text(size=20),
    # facet texts
    strip.text.x = element_text(size=40, face = "bold"),
    strip.text.y = element_text(size=40, face = "bold"))

# print the graph
graph_distribution_pollutant_weekday

# save the graph
ggsave(
  graph_distribution_pollutant_weekday,
  filename = here(
    "3.outputs",
    "1.figures",
    "1.eda",
    "graph_distribution_pollutant_weekday.pdf"
  ),
  width = 90,
  height = 40,
  units = "cm",
  device = cairo_pdf
)
````

# Weather Variables

We explore here the seasonal patterns of weather parameters.

### Monthly Variation in Weather Parameters

We plot the distribution of continuous weather parameters by month:

```{R, echo=TRUE, layout="l-body-outset", fig.width=30, fig.height=10, dev = "CairoPNG"}
# distribution of weather parameters by month
graph_distribution_weather_month <- data %>%
  select(month, rainfall_height, rainfall_duration, temperature_average, humidity_average, wind_speed) %>%
  rename("Rainfall Height (mm)" = rainfall_height,  "Rainfall Duration (min)" = rainfall_duration,
         "Average Temperature (°C)" = temperature_average, "Average Humidity (%)" = humidity_average,
         "Wind Speed (m/s)" = wind_speed) %>%
  pivot_longer(cols = -c(month), names_to = "weather_parameter", values_to = "value") %>%
  ggplot(., aes(x = value, y = reorder(month, desc(month)))) +
  geom_boxplot(colour = "deepskyblue3", size = 1.3) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 5), labels = function(x) format(x, big.mark = " ", scientific = FALSE)) +  
  facet_wrap(~ weather_parameter, scales = "free_x", ncol = 5) +
  xlab("Value") + ylab("") +
  custom_theme

# print the graph
graph_distribution_weather_month

# save the graph
ggsave(graph_distribution_weather_month, filename = here("3.outputs", "1.figures", "1.eda", "graph_distribution_weather_month.pdf"), 
       width = 70, height = 30, units = "cm", device = cairo_pdf)
````

We also plot the distribution of wind direction categories by month:

```{R,echo=TRUE, layout="l-body-outset", fig.width=20, fig.height=10, dev = "CairoPNG"}
# distribution of wind direction by month
graph_distribution_wd_month <- data %>%
  select(month, wind_direction_categories) %>%
  pivot_longer(cols = -c(month),
               names_to = "wind_direction_categories",
               values_to = "categories") %>%
  group_by(month, categories) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n) * 100) %>%
  ggplot(., aes(x = fct_rev(month), y = freq, group = "l")) +
  geom_line(colour = "deepskyblue3", size = 1.4) +
  facet_wrap(~ categories, ncol = 4) +
  coord_flip() +
  xlab("") + ylab("Proportion (%)") +
  custom_theme +
  theme(
    # axis titles parameters
    axis.title.x = element_text(size=40, face = "bold", margin = margin(t = 20, r = 0, b = 0, l =0)),
    axis.title.y = element_text(size=40, face = "bold", margin = margin(t = 0, r = 20, b = 0, l = 0)),
    # axis texts
    axis.text.x = element_text(size=20),
    axis.text.y = element_text(size=20),
    # facet texts
    strip.text.x = element_text(size=40, face = "bold"),
    strip.text.y = element_text(size=40, face = "bold"),
    # margins
    plot.margin = margin(1, 1, 1, -1, "cm"))


# print the graph
graph_distribution_wd_month

# save the graph
ggsave(graph_distribution_wd_month, filename = here("3.outputs", "1.figures", "1.eda", "graph_distribution_wd_month.pdf"), 
       width = 50, height = 20, units = "cm", device = cairo_pdf)
````

### Polar Plot of Wind Direction

We plot the polar plot of wind direction:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=10, fig.height=10, dev = "CairoPNG"}
# create the wind direction proportion data
data_polar_plot_wind_direction <- data %>%
  select(wind_direction) %>%
  mutate(wind_direction = ifelse(wind_direction == 360, 0, wind_direction)) %>%
  group_by(wind_direction) %>%
  # compute the number of observations
  summarise(n = n()) %>%
  # compute the proportion
  mutate(freq = round(n / sum(n)*100, 0))

# make the graph
graph_polar_plot_wind_direction <- ggplot(data_polar_plot_wind_direction, aes(x = as.factor(wind_direction), y = freq, group = "l")) + 
  geom_segment((aes(x = as.factor(wind_direction), xend = as.factor(wind_direction), y = 0, yend = freq)), colour = "deepskyblue3", size = 2, lineend = "round") +
  coord_polar(start = -5*pi/ 180) +
  xlab("") + ylab("Proportion (%)") +
  custom_theme +
  theme(axis.ticks.y = element_line(color="gray42"))

# print the graph
graph_polar_plot_wind_direction

# save the graph
ggsave(graph_polar_plot_wind_direction, filename = here::here("3.outputs", "1.figures", "1.eda", "graph_polar_plot_wind_direction.pdf"), 
       width = 20, height = 20, units = "cm", device = cairo_pdf)
````

### Air Pollutant Concentrations by Wind Direction and Wind Speed

We finally plot the the predicted air pollutant concentrations using the wind components:

```{r, echo = TRUE, results = 'hide'}
# make the polar plots for each pollutant
a <- polarPlot(data, pollutant = "mean_no2_sl", x = "wind_speed", wd = "wind_direction", 
               main = "Average NO2 at Saint-Louis (' * mu * 'g/m' ^3 *')", key.header = "", key.footer = "",
               resolution="fine")

b <- polarPlot(data, pollutant = "mean_no2_l", x = "wind_speed", wd = "wind_direction", 
               main = "Average NO2 at Longchamp (' * mu * 'g/m' ^3 *')", key.header = "", key.footer = "",
               resolution="fine")

c <- polarPlot(data, pollutant = "mean_pm10_sl", x = "wind_speed", wd = "wind_direction", 
               main = "Average PM10 at Saint-Louis (' * mu * 'g/m' ^3 *')", key.header = "", key.footer = "",
               resolution="fine")

d <- polarPlot(data, pollutant = "mean_pm10_l", x = "wind_speed", wd = "wind_direction", 
              main = "Average PM10 at Longchamp (' * mu * 'g/m' ^3 *')", key.header = "", key.footer = "",
               resolution="fine")

e <- polarPlot(data, pollutant = "mean_pm25_l", x = "wind_speed", wd = "wind_direction", 
               main = "Average PM2.5 at Longchamp (' * mu * 'g/m' ^3 *')", key.header = "", key.footer = "",
               resolution="fine")

f <- polarPlot(data, pollutant = "mean_o3_l", x = "wind_speed", wd = "wind_direction", 
               main = "Average O3 at Longchamp (' * mu * 'g/m' ^3 *')", key.header = "", key.footer = "",
               resolution="fine")

g <- polarPlot(data, pollutant = "mean_so2_l", x = "wind_speed", wd = "wind_direction", 
               main = "Average SO2 at Longchamp (' * mu * 'g/m' ^3 *')", key.header = "", key.footer = "",
               resolution="fine")

# save the graph
pdf(here("3.outputs", "1.figures", "1.eda", "graph_polar_plots_pollutants.pdf"), width = 14, height = 5)
print(a, split = c(1, 1, 4, 2), more = TRUE)
print(b, split = c(2, 1, 4, 2), more = TRUE)
print(c, split = c(3, 1, 4, 2), more = TRUE)
print(d, split = c(4, 1, 4, 2), more = TRUE)
print(e, split = c(1, 2, 4, 2), more = TRUE)
print(f, split = c(2, 2, 4, 2), more = TRUE)
print(g, split = c(3, 2, 4, 2), more = FALSE)
dev.off()
````

# Road Traffic

We explore here the seasonal patterns of road traffic.

### Monthly Seasonality of Road Traffic

We plot the distribution of vehicles flow by month:

```{R,echo=TRUE, layout="l-body-outset", fig.width=20, fig.height=10, dev = "CairoPNG"}
# distribution of road traffic by month
graph_distribution_road_traffic_month <- data %>%
  ggplot(., aes(x = road_traffic_flow, y = reorder(month, desc(month)))) +
  geom_boxplot(colour = "deepskyblue3", size = 1.3) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 5), labels = function(x) format(x, big.mark = " ", scientific = FALSE)) +  
  xlab("Daily Average of Hourly Road Traffic Flow (Number of Vehicles)") + ylab("") +
  custom_theme +
  theme(
    axis.title.x = element_text(
      size = 40,
      face = "bold",
      margin = margin(
        t = 20,
        r = 0,
        b = 0,
        l = 0
      )
    ),
    axis.text.x = element_text(size = 26),
    axis.text.y = element_text(size = 26)
  )

# print the graph
graph_distribution_road_traffic_month

# save the graph
ggsave(graph_distribution_road_traffic_month, filename = here("3.outputs", "1.figures", "1.eda", "graph_distribution_road_traffic_month.pdf"), 
       width = 50, height = 30, units = "cm", device = cairo_pdf)
````

### Weekly Variation of Road Traffic

We plot the distribution of vehicles flow by day of the week:

```{R,echo=TRUE, layout="l-body-outset", fig.width=20, fig.height=10, dev = "CairoPNG"}
# density of road traffic by day of the week
graph_distribution_tonnage_weekday <- data %>%
  ggplot(., aes(x = road_traffic_flow, y = reorder(weekday, desc(weekday)))) +
  geom_boxplot(colour = "deepskyblue3", size = 1.3) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 5), labels = function(x) format(x, big.mark = " ", scientific = FALSE)) +  
  xlab("Daily Average of Hourly Road Traffic Flow (Number of Vehicles)") + ylab("") +
  custom_theme +
  theme(
    axis.title.x = element_text(
      size = 40,
      face = "bold",
      margin = margin(
        t = 20,
        r = 0,
        b = 0,
        l = 0
      )
    ),
    axis.text.x = element_text(size = 26),
    axis.text.y = element_text(size = 26)
  )

# print the graph
graph_distribution_tonnage_weekday

# save the graph
ggsave(graph_distribution_tonnage_weekday, filename = here("3.outputs", "1.figures", "1.eda", "graph_distribution_road_traffic_weekday.pdf"), 
       width = 50, height = 30, units = "cm", device = cairo_pdf)
````








