---
title: "Map of Marseille Context"
description: |
  Script for reproducing the map.
author:
  - name: Marie-Abèle Bind 
    url: https://scholar.harvard.edu/marie-abele
    affiliation: Biostatistics Center, Massachusetts General Hospital
    affiliation_url: https://biostatistics.massgeneral.org/faculty/marie-abele-bind-phd/
  - name: Marion Leroutier 
    url: https://www.parisschoolofeconomics.eu/en/leroutier-marion/work-in-progress/
    affiliation: Misum, Stockholm School of Economics
    affiliation_url: https://www.hhs.se/en/persons/l/leroutier-marion/
  - name: Léo Zabrocki 
    url: https://lzabrocki.github.io/
    affiliation: Paris School of Economics
    affiliation_url: https://www.parisschoolofeconomics.eu/fr/zabrocki-leo/
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
      keep_md: true
      toc: true
      toc_depth: 2
---

<style>
body {
text-align: justify}
</style>

In this document, we provide all steps and R codes required to reproduce the figures of Fisherian intervals displayed in the main article. **Should you have any questions, need help to reproduce the analysis or find coding errors, please do not hesitate to contact us at leo.zabrocki@psemail.eu and marion.leroutier@psemail.eu.**

# Required Packages

To reproduce exactly the `script_figures_paper.html` document, we first need to have installed:

* the [R](https://www.r-project.org/) programming language 
* [RStudio](https://rstudio.com/), an integrated development environment for R, which will allow you to knit the `5_script_checking_balance_figures.Rmd` file and interact with the R code chunks
* the [R Markdown](https://rmarkdown.rstudio.com/) package
* and the [Distill](https://rstudio.github.io/distill/) package which provides the template for this document. 

Once everything is set up, we have to load the following packages:

```{r, echo = TRUE, message = FALSE, warning = FALSE}
# load required packages
library(knitr) # for creating the R Markdown document
library(here) # for files paths organization
library(tidyverse) # for data manipulation and visualization
library(osmdata) # for retrieving open street map data
library(sf) # for simple features access
library(Cairo) # for printing customed police of graphs
```

We finally load our customed `ggplot2` theme for graphs:

```{r, echo = TRUE, message = FALSE, warning = FALSE}
# load ggplot customed theme
source(here::here("2.scripts", "4.custom_ggplot2_theme", "script_custom_ggplot_theme_small_wrap.R"))
````

The theme is based on the fantastic [hrbrthemes](https://hrbrmstr.github.io/hrbrthemes/index.html) package. If you do not want to use this theme or are unable to install it because of fonts issues, you can use the `theme_bw()` already included in the `ggplot2` package.

# Gathering the data

### City's boundaries

We downloaded from [data.gouv.fr](https://www.data.gouv.fr/fr/datasets/quartiers-de-marseille-1/#) a shape file of Marseille's districts. We load these data and compute the union of the districts to have the boundaries of the city:

```{R, echo = TRUE}
# load the city's boundaries
marseille_borders <- st_read(here::here("1.data", "1.raw_data", "6.marseille_map_data", "districts_marseille.shp")) %>%
  st_union()
````

### Port's boundaries

Using the `osmdata` package, we retrieve the boundaries of Marseille's port:

```{R, echo = TRUE}
# building the query to get boundaries of the port
harbour_query <- getbb("Marseille") %>%
  opq() %>%
  add_osm_feature("harbour")

# retrieve the data
harbour_data <- osmdata_sf(harbour_query)
````

### Roads data

Using the `osmdata` package, we retrieve Marseille's network of roads. This query takes a bit of time to run:

```{R, echo = TRUE}
# building the query to get roads data
roads_query <- getbb("Marseille") %>%
  opq() %>%
  add_osm_feature("highway")

# retrieve the data
roads_data <- osmdata_sf(roads_query)
````

### Air pollution measuring stations data

We retrieve the coordinates of Longchamp and Saint Louis stations from [AtmoSud](https://www.atmosud.org/) website:

```{R, echo = TRUE}
# create air pollution measuring stations data
data_stations <- tibble(latitude = c(43.34811,  43.30610), longitude = c(5.36012, 5.39526), name = c("Saint Louis", "Longchamp"))

# set the crs
data_stations <- st_as_sf(
  data_stations, 
  coords = c('longitude', 'latitude'),
  crs = "+init=epsg:4326"
)

# retrieve station coordinates for labelling their names on the map
stations_coordinates <- as.data.frame(st_transform(data_stations, 2154) %>%
                                 st_coordinates(.))
stations_coordinates$name <- data_stations$name
````

# Making the map

```{R, echo=TRUE, layout="l-body-outset", fig.width=20, fig.height=20, warning = FALSE, dev = "CairoPNG"}
# we first store a vector of colors to create the legend
colors <- c("Harbour" = "coral", "Stations" = "deepskyblue3")

# make the map
map_marseille <- ggplot() +
  # city's boundaries
  geom_sf(
    data = marseille_borders,
    colour = "black",
    fill = "white",
    size = 0.8
  ) +
  # roads
  geom_sf(data = roads_data$osm_lines,
          colour = "gray80",
          size = 0.2) +
  # station coordinates
  geom_sf(
    data = data_stations,
    aes(colour = "Stations"),
    shape = 3,
    stroke = 2.5,
    size = 8
  ) +
  # port's boundaries
  geom_sf(data = harbour_data$osm_lines,
          aes(colour = "Harbour"),
          size = 1) +
  geom_sf(
    data = harbour_data$osm_polygons,
    aes(colour = "Harbour"),
    fill = NA,
    size = 0.8
  ) +
  # station labels
  ggrepel::geom_text_repel(
    data = stations_coordinates,
    aes(X, Y, label = name),
    point.padding = 1.8,
    segment.color = NA,
    size = 12,
    fontface = 'bold'
  ) +
  # axes labels
  xlab('Longitude') + ylab('Latitude') +
  # add scale
  ggspatial::annotation_scale(
    location = "br",
    line_width = 0.5,
    height = unit(0.2, "cm")
  ) +
  # add north arrow
  ggspatial::annotation_north_arrow(
    location = "tr",
    which_north = "true",
    height = unit(1, "cm"),
    width = unit(1, "cm")
  ) +
  # zoom on the map
  coord_sf(
    crs = st_crs(2154),
    xlim = c(885000, 898500),
    ylim = c(6245000, 6254000),
    expand = FALSE
  ) +
  scale_color_manual(name = "Legend:", values = colors) +
  custom_theme +
  # theme options
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 0.8),
    panel.background = element_rect(fill = "aliceblue"),
    panel.grid.major = element_blank(),
    # axis titles parameters
    axis.title.x = element_text(
      size = 36,
      face = "bold",
      margin = margin(
        t = 20,
        r = 0,
        b = 0,
        l = 0
      )
    ),
    axis.title.y = element_text(
      size = 36,
      face = "bold",
      margin = margin(
        t = 0,
        r = 20,
        b = 0,
        l = 0
      )
    ),
    # axis texts
    axis.text.x = element_text(size = 20),
    axis.text.y = element_text(size = 20),
    # facet texts
    strip.text.x = element_text(size = 36, face = "bold"),
    strip.text.y = element_text(size = 36, face = "bold"),
    # legend parameters
    legend.position = "top",
    legend.justification = "left",
    legend.direction = "horizontal",
    legend.title = element_text(size = 36, face = "bold"),
    legend.text = element_text(size = 28)
  )

# save the map
ggsave(
  map_marseille,
  filename = here::here("3.outputs", "1.figures", "1.eda", "map_marseille.pdf"),
  width = 40,
  height = 28,
  units = "cm",
  device = cairo_pdf
)
````