---
title: "Exploratory Data Analysis"
description: |
  Hourly Level Data.
author:
  - name: Marie-Abèle Bind 
    url: https://scholar.harvard.edu/marie-abele
    affiliation: Biostatistics Center, Massachusetts General Hospital
    affiliation_url: https://biostatistics.massgeneral.org/faculty/marie-abele-bind-phd/
  - name: Marion Leroutier 
    url: https://www.parisschoolofeconomics.eu/en/leroutier-marion/work-in-progress/
    affiliation: Misum, Stockholm School of Economics
    affiliation_url: https://www.hhs.se/en/persons/l/leroutier-marion/
  - name: Léo Zabrocki 
    url: https://lzabrocki.github.io/
    affiliation: Paris School of Economics
    affiliation_url: https://www.parisschoolofeconomics.eu/fr/zabrocki-leo/
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
      keep_md: true
      toc: true
      toc_depth: 2
---

<style>
body {
text-align: justify}
</style>


In this document, we provide all steps to reproduce the exploratory analysis of our data at the hourley. **Should you have any questions or find errors, please do not hesitate to contact us at leo.zabrocki@psemail.eu and marion.leroutier@psemail.eu**

# Required Packages

To reproduce exactly the `script_data_wrangling.hmtl` document, you first need to have installed:

* the [R](https://www.r-project.org/) programming language on your computer 
* [RStudio](https://rstudio.com/), an integrated development environment for R, which will allow you to knit the `script_data_wrangling.Rmd` file and interact with the R code chunks
* the [R Markdown](https://rmarkdown.rstudio.com/) package
* and the [Distill](https://rstudio.github.io/distill/) package which provides the template of this document. 

Once everything is set up, we need to load the following packages:

```{r, echo=TRUE, message = FALSE, warning = FALSE}
# load required packages
library(rmarkdown) # for creating the R Markdown document
library(knitr) # for creating the R Markdown document
library(here) # for files paths organization
library(tidyverse) # for data manipulation and visualization
library(ggridges) # for density ridge plots
library(patchwork) # for combining plots
library(Cairo) # for printing customed police of graphs
```

We also load our custom `ggplot2` theme for graphs:

```{r, echo=TRUE, message = FALSE, warning = FALSE}
# load ggplot customed theme
source(here::here("2.scripts", "4.custom_ggplot2_theme", "script_custom_ggplot_theme.R"))
````

The theme is based on the fantastic [hrbrthemes](https://hrbrmstr.github.io/hrbrthemes/index.html) package. If you do not want to use this theme or are unable to install it because of fonts issues, you can use the `theme_mimimal()` included in the `ggplot2` package.

Finally, we load the data: 

```{r, echo=TRUE, message = FALSE, warning = FALSE}
# load data
data <- readRDS(here::here("1.data", "2.data_for_analysis", "0.main_data", "data_for_analysis_hourly.RDS"))
````

# Vessel Traffic Data

We first explore the patterns of vessel traffic data at the hourly level and by vessel type (cruise, ferry and other types).

### Hourly Patterns of Gross Tonnage 

Mean of total tonnage by vessel categories and hour of the day:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=20, fig.height=10, dev = "CairoPNG"}
# create the graph
graph_total_tonnage_hour_vessel_type <- data %>%
  select(hour, total_gross_tonnage, total_gross_tonnage_cruise, total_gross_tonnage_ferry, total_gross_tonnage_other_vessels) %>%
  rename("Total Tonnage" = total_gross_tonnage, "Cruise Tonnage" = total_gross_tonnage_cruise, "Ferry Tonnage" =total_gross_tonnage_ferry, "Other Vessel Types Tonnage" = total_gross_tonnage_other_vessels) %>%
  pivot_longer(cols = -c(hour), names_to = "tonnage_type", values_to = "tonnage") %>%
  group_by(tonnage_type, hour) %>%
  summarise(mean_tonnage = mean(tonnage) %>%
              ifelse(is.na(.), 0, .)) %>%
  ggplot(., aes(x = as.factor(hour), y = mean_tonnage, group = "l")) + 
  geom_line(colour = "deepskyblue3", size = 1.6) +
  facet_wrap(~ tonnage_type) +
  xlab("Hour") + ylab("Average Gross Tonnage") +
  custom_theme

# display the graph
graph_total_tonnage_hour_vessel_type

ggsave(graph_total_tonnage_hour_vessel_type, filename = here::here("3.outputs", "1.figures", "1.eda", "graph_total_tonnage_hour_vessel_type.pdf"), 
       width = 45, height = 20, units = "cm", device = cairo_pdf)
````

Mean of entering and exiting total tonnage by vessel categories and hour of the day:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=20, fig.height=10, dev = "CairoPNG"}
# create the graph
graph_entering_exiting_total_tonnage_hour_vessel_type <- data %>%
  select(hour, total_gross_tonnage_entry:total_gross_tonnage_entry_other_vessels,
         total_gross_tonnage_exit:total_gross_tonnage_exit_other_vessels) %>%
  pivot_longer(cols = -c(hour), names_to = "tonnage_type", values_to = "tonnage") %>%
  mutate(entry_exit = ifelse(str_detect(tonnage_type, "entry"), "Arrival", "Departure"),
         vessel_type = "Total Tonnage" %>%
           ifelse(str_detect(tonnage_type, "cruise"), "Cruise", .) %>%
           ifelse(str_detect(tonnage_type, "ferry"), "Ferry", .) %>%
           ifelse(str_detect(tonnage_type, "other"), "Other Vessel Types", .)) %>%
  group_by(vessel_type, entry_exit, hour) %>%
  summarise(mean_tonnage = mean(tonnage) %>%
              ifelse(is.na(.), 0, .)) %>%
  ggplot(., aes(x = as.factor(hour), y = mean_tonnage, group = entry_exit, colour = entry_exit)) + 
  geom_line(size = 1.6) +
  scale_colour_manual(values = c("deepskyblue3", "tomato")) +
  facet_wrap(~ vessel_type) +
  xlab("Hour") + ylab("Average Gross Tonnage") +
  labs(colour = "Vessel Status") +
  custom_theme +
  theme(legend.position = "top", legend.justification = "left", legend.direction = "horizontal")

# display the graph
graph_entering_exiting_total_tonnage_hour_vessel_type

ggsave(graph_entering_exiting_total_tonnage_hour_vessel_type, filename = here::here("3.outputs", "1.figures", "1.eda", "graph_entering_exiting_total_tonnage_hour_vessel_type.pdf"), 
       width = 45, height = 20, units = "cm", device = cairo_pdf)
````

### Hourly Patterns of total Gross Tonnage by Season

Mean of total tonnage by vessel categories, season and hour of the day:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=40, fig.height=12, dev = "CairoPNG"}
# create the graph
graph_total_tonnage_season_hour_vessel_type <- data %>%
  mutate(season = recode(season, "1" = "January-March", "2" = "April-June", "3" = "July-September", "4" = "October-December") %>% fct_relevel(., "January-March", "April-June", "July-September","October-December")) %>%
  select(hour, season, total_gross_tonnage_cruise, total_gross_tonnage_ferry, total_gross_tonnage_other_vessels) %>%
  rename("Cruise" = total_gross_tonnage_cruise, "Ferry" =total_gross_tonnage_ferry, "Other Vessel Types" = total_gross_tonnage_other_vessels) %>%
  pivot_longer(cols = -c(hour, season), names_to = "tonnage_type", values_to = "tonnage") %>%
  group_by(tonnage_type, season, hour) %>%
  summarise(mean_tonnage = mean(tonnage) %>%
              ifelse(is.na(.), 0, .)) %>%
  ggplot(., aes(x = as.factor(hour), y = mean_tonnage, group = "l")) + 
  geom_line(colour = "deepskyblue3", size = 1.6) +
  facet_grid(tonnage_type ~ season, scales = "free_y") +
  xlab("Hour") + ylab("Average Gross Tonnage") +
  custom_theme +
  theme(    
    # axis titles parameters
    axis.title.x = element_text(size=32, face = "bold", margin = margin(t = 20, r = 0, b = 0, l =0)),
    axis.title.y = element_text(size=32, face = "bold", margin = margin(t = 0, r = 20, b = 0, l = 0)),
    # facet texts
    strip.text.x = element_text(size=32, face = "bold"),
    strip.text.y = element_text(size=32, face = "bold"))

# display the graph
graph_total_tonnage_season_hour_vessel_type

# save the graph
ggsave(graph_total_tonnage_season_hour_vessel_type, filename = here::here("3.outputs", "1.figures", "1.eda", "graph_total_tonnage_season_hour_vessel_type.pdf"), 
       width = 90, height = 36, units = "cm", device = cairo_pdf)
````

### Lack of Variation in Vessel Traffic

One issue of for our matching analysis is that vessel traffic is very regular. For instance, cruise vessels dock and leave the port for specific days and hours so that it is hard to find similar pairs of hours with and without traffic. We plot below the hourly tonnage of cruise docking the port for mondays belonging to July and August months of 2012:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=34, fig.height=10, dev = "CairoPNG"}
# create the data
data_tonnage_cruise_traffic_monday_season_3_2012 <- data %>%
  filter(month %in% c("July", "August") & year == 2012 & weekday == "Monday") %>%
  mutate(julian_date = lubridate::yday(date)) %>%
  mutate(julian_date = map(julian_date, ~ paste("Day", ., sep = " "))) %>%
  unnest(julian_date) %>%
  select(julian_date, hour, total_gross_tonnage_entry_cruise) 

# graph entering tonnage cruise
graph_tonnage_variation_cruise <- data_tonnage_cruise_traffic_monday_season_3_2012 %>% 
  ggplot(., aes(x = as.factor(hour), y = total_gross_tonnage_entry_cruise, group = julian_date)) + 
  geom_line(colour = "deepskyblue3", size = 3) +
  facet_wrap(~ julian_date) +
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  xlab("Hour") + ylab("Average Gross Tonnage") +
  custom_theme +
  theme(
    # axis titles parameters
    axis.title.x = element_text(size=42, face = "bold", margin = margin(t = 20, r = 0, b = 0, l =0)),
    axis.title.y = element_text(size=42, face = "bold", margin = margin(t = 0, r = 20, b = 0, l = 0)),
    # facet texts
    strip.text.x = element_text(size=40, face = "bold"),
    strip.text.y = element_text(size=40, face = "bold"),
    # axis texts
    axis.text.x = element_text(size=28),
    axis.text.y = element_text(size=28))

# display the graph entering tonnage cruise
graph_tonnage_variation_cruise

ggsave(graph_tonnage_variation_cruise, filename = here::here("3.outputs", "1.figures", "1.eda", "graph_tonnage_variation_cruise.pdf"), 
       width = 84, height = 35, units = "cm", device = cairo_pdf)
````

# Pollution Data

We explore here the hourly patterns of pollutant concentrations. We plot below the average concentration by hour for each pollutant:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=40, fig.height=12, dev = "CairoPNG"}
# creat the graph of pollutants' concentration by hour of the day
graph_pollutant_hour <- data %>%
  select(hour, mean_no2_l:mean_pm10_sl) %>%
  rename("NO2 Longchamp" = mean_no2_l, "O3 Longchamp" = mean_o3_l, "PM2.5 Longchamp" = mean_pm25_l,
         "PM10 Longchamp" = mean_pm10_l, "SO2 Longchamp" = mean_so2_l, "NO2 Saint-Louis" = mean_no2_sl,
         "PM10 Saint-Louis" = mean_pm10_sl) %>%
  pivot_longer(cols = -c(hour), names_to = "pollutant", values_to = "concentration") %>%
  group_by(hour, pollutant) %>%
  summarise(mean_concentration = mean(concentration)) %>%
  ggplot(., aes(x = as.factor(hour), y = mean_concentration, group = "l")) + 
  geom_line(colour = "deepskyblue3", size = 2) +
  facet_wrap(~ pollutant, scales = "free", ncol = 4) +
  xlab("Hour") + ylab("Concentration (µg/m³)") +
  custom_theme +
    theme(
    # axis titles parameters
    axis.title.x = element_text(size=42, face = "bold", margin = margin(t = 20, r = 0, b = 0, l =0)),
    axis.title.y = element_text(size=42, face = "bold", margin = margin(t = 0, r = 20, b = 0, l = 0)),
    # axis texts
    axis.text.x = element_text(size=20),
    axis.text.y = element_text(size=20),
    # facet texts
    strip.text.x = element_text(size=42, face = "bold"),
    strip.text.y = element_text(size=42, face = "bold"))

# display the graph
graph_pollutant_hour

# save the graph
ggsave(graph_pollutant_hour, filename = here::here("3.outputs", "1.figures", "1.eda", "graph_pollutant_hour.pdf"), 
       width = 100, height = 30, units = "cm", device = cairo_pdf)
````

# Weather Data

We explore here the hourly patterns of weather parameters. We plot the hourly distribution of weather parameters:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=20, fig.height=10, dev = "CairoPNG"}
# make the graph
graph_continuous_weather_hour <- data %>%
  select(hour, temperature_average, rainfall_height_dummy, wind_speed, humidity_average) %>%
  rename("Average Temperature (°C)" = temperature_average, "Rainfall Dummy (%)" = rainfall_height_dummy, "Wind Speed (m/s)" =          wind_speed, "Average Humidity (%)" = humidity_average) %>%
  pivot_longer(cols = -c(hour), names_to = "weather_parameter", values_to = "values") %>%
  group_by(weather_parameter, hour) %>%
  summarise(values = mean(values)) %>%
  ungroup() %>%
  mutate(values = ifelse(weather_parameter == "Rainfall Dummy (%)", values*100, values)) %>%
  ggplot(., aes(x = as.factor(hour), y = values, group = "l")) + 
  geom_line(colour = "deepskyblue3", size = 1.4) +
  facet_wrap(~ weather_parameter, scales = "free_y") +
  xlab("Hour") + ylab("Value") +
  custom_theme +
  theme(
    # axis titles parameters
    axis.title.x = element_text(size=36, face = "bold", margin = margin(t = 20, r = 0, b = 0, l =0)),
    axis.title.y = element_text(size=36, face = "bold", margin = margin(t = 0, r = 20, b = 0, l = 0)),
    # axis texts
    axis.text.x = element_text(size=25),
    axis.text.y = element_text(size=25),
    # facet texts
    strip.text.x = element_text(size=36, face = "bold"),
    strip.text.y = element_text(size=36, face = "bold"))
  
# display the graph
graph_continuous_weather_hour

# save the graph
ggsave(graph_continuous_weather_hour, filename = here::here("3.outputs", "1.figures", "1.eda", "graph_continuous_weather_hour.pdf"), 
       width = 60, height = 25, units = "cm", device = cairo_pdf)
````

We plot the hourly distribution of wind direction categories:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=30, fig.height=15, dev = "CairoPNG"}
# make the graph
graph_wind_direction_hour <- data %>%
  select(hour, wind_direction) %>%
  mutate(wind_direction_categories = cut(wind_direction, breaks = seq(0, 360, by  = 90), include.lowest = TRUE) %>%
           recode(., "[0,90]" = "North-East",
                  "(90,180]" = "South-East",
                  "(180,270]" = "South-West",
                  "(270,360]" = "North-West")) %>%
  mutate(hour = as.factor(hour)) %>%
  group_by(hour, wind_direction_categories) %>%
  # compute the number of observations
  summarise(n = n()) %>%
  # compute the proportion
  mutate(freq = round(n / sum(n)*100, 0)) %>%
  ggplot(., aes(x = hour, y = freq, group = "l")) + 
  geom_line(colour = "deepskyblue3", size = 1.4) +
  facet_wrap(~ wind_direction_categories, ncol = 4) +
  coord_flip() +
  xlab("Hour") + ylab("Proportion (%)") +
  custom_theme

# display the graph
graph_wind_direction_hour

# save the graph
ggsave(graph_wind_direction_hour, filename = here::here("3.outputs", "1.figures", "1.eda", "graph_wind_direction_hour.pdf"), 
       width = 40, height = 22, units = "cm", device = cairo_pdf)
````


# Road Traffic Data

We explore here the hourly patterns of the flow of vehicles. We plot below the average flow of vehicles by hour of the day:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=20, fig.height=8, dev = "CairoPNG"}
# create the graph of the flow of vehicles by hour of the day
graph_road_traffic_hour <- data %>%
  group_by(hour) %>%
  summarise(mean_road_traffic_flow = mean(road_traffic_flow, na.rm = TRUE)) %>%
  ungroup() %>%
  ggplot(., aes(x = as.factor(hour), y = mean_road_traffic_flow, group = "l")) + 
  geom_line(colour = "deepskyblue3", size = 2) +
  xlab("Hour") + ylab("Average Road Traffic Flow\n (Number of Vehicles)") +
  custom_theme

# display the graph
graph_road_traffic_hour

# save the graph
ggsave(graph_road_traffic_hour, filename = here::here("3.outputs", "1.figures", "1.eda", "graph_road_traffic_hour.pdf"), 
       width = 30, height = 15, units = "cm", device = cairo_pdf)
````
