---
title: "Checking the Hypothetical Intervention - Cruise Experiment"
description: |
  Comparing days with one cruise vessels entering the port to days without. Adjusting for calendar and weather indicators.
authors:
  - name: Léo Zabrocki 
    url: https://www.parisschoolofeconomics.eu/en/
    affiliation: Paris School of Economics
    affiliation_url: https://www.parisschoolofeconomics.eu/en/
  - name: Marion Leroutier 
    url: https://marionleroutier.weebly.com/
    affiliation: Mistra Center for Sustainable Markets, Stockholm School of Economics
    affiliation_url: https://www.hhs.se/en/persons/l/leroutier-marion/
  - name: Marie-Abèle Bind 
    url: https://biostatistics.massgeneral.org/faculty/marie-abele-bind-phd/
    affiliation: Biostatistics Center, Massachusetts General Hospital
    affiliation_url: https://biostatistics.massgeneral.org/faculty/marie-abele-bind-phd/
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
      toc: true
      toc_depth: 3
---

<style>
body {
text-align: justify}
</style>

In this document, we take great care providing all steps and R codes required to check the intervention we set up in our matching procedure.  We compare days where:

* treated units are days with one cruise vessel entering the port in *t*.
* control units are day with zero cruise vessel entering the port in *t*.

We adjust for calendar indicator and weather confouding factors.

**Should you have any questions, need help to reproduce the analysis or find coding errors, please do not hesitate to contact us at leo.zabrocki@psemail.eu and marion.leroutier@hhs.se.** 

# Required Packages

To reproduce exactly the `3_script_checking_intervention.html` document, we first need to have installed:

* the [R](https://www.r-project.org/) programming language 
* [RStudio](https://rstudio.com/), an integrated development environment for R, which will allow you to knit the `3_script_checking_intervention.Rmd` file and interact with the R code chunks
* the [R Markdown](https://rmarkdown.rstudio.com/) package
* and the [Distill](https://rstudio.github.io/distill/) package which provides the template for this document. 

Once everything is set up, we have to load the following packages:

```{r, echo = TRUE, message = FALSE, warning = FALSE}
# load required packages
library(knitr) # for creating the R Markdown document
library(here) # for files paths organization
library(tidyverse) # for data manipulation and visualization
library(ggridges) # for ridge density plots
library(Cairo) # for printing customed police of graphs
library(patchwork) # combining plots
```

We finally load our customed `ggplot2` theme for graphs:

```{r, echo = TRUE, message = FALSE, warning = FALSE}
# load ggplot customed theme
source(here::here("2.scripts", "5.custom_ggplot2_theme", "script_custom_ggplot_theme.R"))
````

The theme is based on the fantastic [hrbrthemes](https://hrbrmstr.github.io/hrbrthemes/index.html) package. If you do not want to use this theme or are unable to install it because of fonts issues, you can use the `theme_bw()` already included in the `ggplot2` package.

# Preparing the Data

We load the matched data:

```{R, echo = TRUE}
# load matched data
data_matched <- readRDS(here::here("1.data", "2.data_for_analysis", "1.cruise_experiment", "matched_data.rds"))
```

# Checking the Hypothetical Intervention

We compute the difference in the daily cruise total gross tonnage for each pair:

```{R, echo=TRUE, message = FALSE, warning = FALSE}
# compute the difference in tonnage by pair
pair_difference_tonnage_t <- data_matched %>%
  select(total_gross_tonnage_cruise, is_treated, pair_number) %>%
  arrange(pair_number, is_treated) %>%
  select(-is_treated) %>%
  group_by(pair_number) %>%
  summarise(tonnage_difference = total_gross_tonnage_cruise[2]- total_gross_tonnage_cruise[1])
````

We find on average, a `r round(mean(pair_difference_tonnage_t$tonnage_difference),0)` difference in gross tonnage between treated and control units. Below is the distribution of the pair difference in hourly gross tonnage in t:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=14, fig.height=10, dev = "CairoPNG"}
# plot the graph
graph_tonnage_difference_density <- ggplot(pair_difference_tonnage_t, aes(x = tonnage_difference)) +
  geom_density(colour = "black", fill = "deepskyblue3", size = 1.1, alpha = 0.8) +
  geom_vline(xintercept = mean(pair_difference_tonnage_t$tonnage_difference), size = 1.1, color = "coral") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 8), labels = function(x) format(x, big.mark = " ", scientific = FALSE)) +
  xlab("Pair Difference in Tonnage") + ylab("Density") +
  custom_theme

# we print the graph
graph_tonnage_difference_density

# save the graph
ggsave(graph_tonnage_difference_density, filename = here::here("3.outputs", "1.figures", "2.analysis_pollution", "1.cruise_experiment", "1.checking_matching_procedure", "graph_tonnage_difference_cruise_tonnage_density.pdf"), 
       width = 30, height = 20, units = "cm", device = cairo_pdf)
````

To check which hypothetical intervention we study, we plot below the average tonnage for each day and for treated and control groups :

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=25, fig.height=18, dev = "CairoPNG"}
# compute mean tonnage for each day
data_mean_tonnage_day <- data_matched %>%
  # select relevant variables
  select(pair_number, is_treated, contains("total_gross_tonnage_cruise")) %>%
  # transform data in long format
  pivot_longer(cols = -c(pair_number, is_treated), names_to = "variable", values_to = "tonnage") %>%
  # create the day variable
  mutate(time = 0 %>%
           ifelse(str_detect(variable, "lag_1"), -1, .) %>%
           ifelse(str_detect(variable, "lag_2"), -2, .) %>%
           ifelse(str_detect(variable, "lag_3"), -3, .) %>%
           ifelse(str_detect(variable, "lag_4"), -4, .) %>%
           ifelse(str_detect(variable, "lag_5"), -5, .) %>%
           ifelse(str_detect(variable, "lag_6"), -6, .) %>%
           ifelse(str_detect(variable, "lead_1"), 1, .) %>%
           ifelse(str_detect(variable, "lead_2"), 2, .) %>%
           ifelse(str_detect(variable, "lead_3"), 3, .) %>%
           ifelse(str_detect(variable, "lead_4"), 4, .) %>%
           ifelse(str_detect(variable, "lead_5"), 5, .) %>%
           ifelse(str_detect(variable, "lead_6"), 6, .)) %>%
  # rename the labels of the is_treated dummy
  mutate(is_treated = ifelse(is_treated == TRUE, "Treated", "Control")) %>%
  # compute the mean tonnage for each day and pollutant
  group_by(variable, is_treated, time) %>%
  summarise(tonnage = mean(tonnage, na.rm = TRUE))

# plot the graph
graph_mean_tonnage_day<- ggplot(data_mean_tonnage_day, aes(x=as.factor(time), y = tonnage, group = is_treated, colour = is_treated, fill = is_treated))  +
  geom_segment(
    x = 2,
    y = 0,
    xend = 2,
    yend = 220233,
    lineend = "round",
    # See available arrow types in example above
    linejoin = "round",
    size = 0.5,
    colour = "black"
  ) +
  geom_line() +
  geom_point(shape = 21,
             size = 8,
             colour = "black") +
  scale_colour_manual(values = c("deepskyblue3", "tomato")) +
  scale_fill_manual(values = c("deepskyblue3", "tomato")) +
  scale_y_continuous(
    breaks = scales::pretty_breaks(n = 5),
    labels = function(x)
      format(x, big.mark = " ", scientific = FALSE)
  ) +
  labs(fill = "Group:") +
  xlab("Day") + ylab("Daily Cruise Gross Tonnage") +
  custom_theme +
  guides(color = FALSE) +
  theme(
    # axis titles parameters
    axis.title.x = element_text(size=40, face = "bold", margin = margin(t = 20, r = 0, b = 0, l =0)),
    axis.title.y = element_text(size=40, face = "bold", margin = margin(t = 0, r = 20, b = 0, l = 0)),
    # axis texts
    axis.text.x = element_text(size=30),
    axis.text.y = element_text(size=30),
    # facet texts
    strip.text.x = element_text(size=40, face = "bold"),
    strip.text.y = element_text(size=40, face = "bold"),
    # legend parameters
    legend.position = "top",
    legend.justification = "left",
    legend.direction = "horizontal"
  )

# we print the graph
graph_mean_tonnage_day

# save the graph
graph_mean_tonnage_day <- graph_mean_tonnage_day +
  theme(plot.title = element_blank())

ggsave(graph_mean_tonnage_day, filename = here::here("3.outputs", "1.figures", "2.analysis_pollution", "1.cruise_experiment", "1.checking_matching_procedure", "graph_mean_cruise_tonnage_day.pdf"), 
       width = 60, height = 30, units = "cm", device = cairo_pdf)
````


# Checking Other Vessels' Types Traffic Evolution

We also check how the difference in tonnage for other vessels' types between treated and control units evolves:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=25, fig.height=10, dev = "CairoPNG"}
# we create a table with the tonnage for each pair, 
# for each vessel type, 
# and for -6 hours to + 6 hours
data_vessel_type_tonnage <- data_matched %>%
  # relabel treatment indicator
  mutate(is_treated = ifelse(is_treated == TRUE, "treated", "control")) %>%
  # select relevant variables
  select(pair_number, is_treated, contains("total_gross_tonnage_cruise"),
         contains("total_gross_tonnage_ferry"), contains("total_gross_tonnage_other_boat")) %>%
  # transform data in long format
  pivot_longer(cols = -c(pair_number, is_treated), names_to = "variable", values_to = "tonnage") %>%
  # create vessel type variable
  mutate(vessel_type = NA %>%
           ifelse(str_detect(variable, "cruise"), "Cruise",.) %>%
           ifelse(str_detect(variable, "ferry"), "Ferry",.) %>% 
           ifelse(str_detect(variable, "other_boat"), "Other Types of Vessels",.)) %>%
  mutate(time = 0 %>%
           ifelse(str_detect(variable, "lag_1"), -1, .) %>%
           ifelse(str_detect(variable, "lag_2"), -2, .) %>%
           ifelse(str_detect(variable, "lag_3"), -3, .) %>%
           ifelse(str_detect(variable, "lag_4"), -4, .) %>%
           ifelse(str_detect(variable, "lag_5"), -5, .) %>%
           ifelse(str_detect(variable, "lag_6"), -6, .) %>%
           ifelse(str_detect(variable, "lead_1"), 1, .) %>%
           ifelse(str_detect(variable, "lead_2"), 2, .) %>%
           ifelse(str_detect(variable, "lead_3"), 3, .) %>%
           ifelse(str_detect(variable, "lead_4"), 4, .) %>%
           ifelse(str_detect(variable, "lead_5"), 5, .) %>%
           ifelse(str_detect(variable, "lead_6"), 6, .)) %>%
  select(pair_number, vessel_type, is_treated, time, tonnage) %>% 
  pivot_wider(names_from = is_treated, values_from = tonnage)

# compute the average difference in traffic between treated and control units
data_mean_difference <- data_vessel_type_tonnage %>%
  mutate(difference = treated-control) %>%
  select(-c(treated, control)) %>%
  group_by(vessel_type, time) %>%
  summarise(mean_difference = mean(difference, na.rm = TRUE)) %>%
  ungroup()

# plot the evolution
graph_tonnage_difference_vessel_type <-
  ggplot(data_mean_difference,
         aes(x = as.factor(time), y = mean_difference, group = "l"))  +
  geom_hline(yintercept = 0) +
  geom_segment(aes(
    x = as.factor(time),
    xend = as.factor(time),
    y = 0,
    yend = mean_difference
  )) +
  geom_point(
    shape = 21,
    size = 8,
    colour = "black",
    fill = "deepskyblue3"
  ) +
  scale_y_continuous(
    breaks = scales::pretty_breaks(n = 5),
    labels = function(x)
      format(x, big.mark = " ", scientific = FALSE)
  ) +
  facet_wrap(~ vessel_type) +
  xlab("Day") + ylab("Average Difference in\n Total Gross Tonnage") +
  custom_theme +
  theme(
    # axis titles parameters
    axis.title.x = element_text(size=40, face = "bold", margin = margin(t = 20, r = 0, b = 0, l =0)),
    axis.title.y = element_text(size=40, face = "bold", margin = margin(t = 0, r = 20, b = 0, l = 0)),
    # axis texts
    axis.text.x = element_text(size=30),
    axis.text.y = element_text(size=30),
    # facet texts
    strip.text.x = element_text(size=40, face = "bold"),
    strip.text.y = element_text(size=40, face = "bold"),
    # legend parameters
    legend.position = "top",
    legend.justification = "left",
    legend.direction = "horizontal",
    legend.title = element_text(size=40, face = "bold"),
    legend.text = element_text(size=30)
  )

# we print the graph
graph_tonnage_difference_vessel_type

# save the graph
ggsave(graph_tonnage_difference_vessel_type, filename = here::here("3.outputs", "1.figures", "2.analysis_pollution", "1.cruise_experiment", "1.checking_matching_procedure", "graph_tonnage_difference_vessel_type.pdf"), 
       width = 60, height = 20, units = "cm", device = cairo_pdf)
```` 

