---
title: "Checking Covariates Balance"
description: |
  Comparing days with one cruise vessels entering the port to days without. Adjusting for calendar and weather indicators.
authors:
  - name: Léo Zabrocki 
    url: https://www.parisschoolofeconomics.eu/en/
    affiliation: Paris School of Economics
    affiliation_url: https://www.parisschoolofeconomics.eu/en/
  - name: Marion Leroutier 
    url: https://marionleroutier.weebly.com/
    affiliation: Mistra Center for Sustainable Markets, Stockholm School of Economics
    affiliation_url: https://www.hhs.se/en/persons/l/leroutier-marion/
  - name: Marie-Abèle Bind 
    url: https://biostatistics.massgeneral.org/faculty/marie-abele-bind-phd/
    affiliation: Biostatistics Center, Massachusetts General Hospital
    affiliation_url: https://biostatistics.massgeneral.org/faculty/marie-abele-bind-phd/
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
      toc: true
      toc_depth: 3
---

<style>
body {
text-align: justify}
</style>

In this document, we take great care providing all steps and R codes required to check whether our most matching procedure achieved balance.  We compare days where:

* treated units are days with one cruise vessel entering the port in *t*.
* control units are day with zero cruise vessel entering the port in *t*.

We adjust for calendar indicator and weather confouding factors.

**Should you have any questions, need help to reproduce the analysis or find coding errors, please do not hesitate to contact us at leo.zabrocki@psemail.eu and marion.leroutier@hhs.se.**

# Required Packages

To reproduce exactly the `4_script_checking_balance_figures.html` document, we first need to have installed:

* the [R](https://www.r-project.org/) programming language 
* [RStudio](https://rstudio.com/), an integrated development environment for R, which will allow you to knit the `5_script_checking_balance_figures.Rmd` file and interact with the R code chunks
* the [R Markdown](https://rmarkdown.rstudio.com/) package
* and the [Distill](https://rstudio.github.io/distill/) package which provides the template for this document. 

Once everything is set up, we have to load the following packages:

```{r, echo = TRUE, message = FALSE, warning = FALSE}
# load required packages
library(knitr) # for creating the R Markdown document
library(here) # for files paths organization
library(tidyverse) # for data manipulation and visualization
library(ggridges) # for ridge density plots
library(Cairo) # for printing customed police of graphs
library(patchwork) # combining plots
library(Matching) # check covariate balance
```

We finally load our customed `ggplot2` theme for graphs:

```{r, echo = TRUE, message = FALSE, warning = FALSE}
# load ggplot customed theme
source(here::here("2.scripts", "5.custom_ggplot2_theme", "script_custom_ggplot_theme.R"))
````

The theme is based on the fantastic [hrbrthemes](https://hrbrmstr.github.io/hrbrthemes/index.html) package. If you do not want to use this theme or are unable to install it because of fonts issues, you can use the `theme_bw()` already included in the `ggplot2` package.

# Preparing the Data

We load the matched data:

```{R, echo = TRUE}
# load matched data
data_matched <- readRDS(here::here("1.data", "2.data_for_analysis",  "1.cruise_experiment", "matched_data.rds"))
```

# Figures for Covariates Distribution for Treated and Control Units

We check whether coviariates balance was achieved with the thresholds we defined for our matching procedure. We plot distributions of weather and calendar variables (Lags 0-1) and pollutants (Lag 1) for treated and control groups.

### Weather Covariates

For continuous weather covariates, we draw boxplots for treated and control groups:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=20, fig.height=20, dev = "CairoPNG"}
# we select control variables and store them in a long dataframe
data_weather_continuous_variables <- data_matched %>%
  dplyr::select(temperature_average, temperature_average_lag_1,
         humidity_average, humidity_average_lag_1,
         wind_speed, wind_speed_lag_1,
         is_treated) %>%
  pivot_longer(cols = -c(is_treated), names_to = "variable", values_to = "values") %>%
  mutate(new_variable = NA %>%
           ifelse(str_detect(variable, "temperature_average"), "Average Temperature (°C)",.) %>%
           ifelse(str_detect(variable, "humidity_average"), "Humidity Average (%)",.) %>%
           ifelse(str_detect(variable, "wind_speed"), "Wind Speed (m/s)",.)) %>%
  mutate(time = "in t" %>%
           ifelse(str_detect(variable, "lag_1"), "in t-1", .)) %>%
  mutate(variable = paste(new_variable, time, sep = " ")) %>%
  mutate(is_treated = if_else(is_treated==TRUE, "Treated", "Control"))

graph_boxplot_continuous_weather <- ggplot(data_weather_continuous_variables, aes(x = is_treated, y = values, colour = is_treated)) + 
  geom_violin(size = 2) + 
  geom_boxplot(width=0.1, outlier.shape=NA) +
  scale_color_manual(values=c("deepskyblue3", "coral")) +
  ylab("Covariate Value") +
  xlab("") + 
  labs(colour = "Units Status:") +
  facet_wrap(~variable, scale = "free", ncol = 2) +
  custom_theme +
  theme(legend.position = "top", legend.justification = "left", legend.direction = "horizontal")

# we print the graph
graph_boxplot_continuous_weather

# save the graph
ggsave(graph_boxplot_continuous_weather, filename = here::here("3.outputs", "1.figures", "2.analysis_pollution", "1.cruise_experiment", "1.checking_matching_procedure", "graph_boxplot_continuous_weather.pdf"), width = 60, height = 60, units = "cm", device = cairo_pdf)
````

For the rainfall dummy and the wind direction categories, we plot the proportions:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=30, fig.height=15, dev = "CairoPNG"}
# we select the rainfall variables
data_weather_categorical <- data_matched %>%
  dplyr::select(rainfall_height_dummy, rainfall_height_dummy_lag_1,
         wind_direction_categories, wind_direction_categories_lag_1,
         is_treated) %>%
 mutate_at(vars(rainfall_height_dummy:rainfall_height_dummy_lag_1), ~ ifelse(.==1, "True", "False")) %>%
  mutate_all(~ as.character(.)) %>%
  pivot_longer(cols = -c(is_treated), names_to = "variable", values_to = "values") %>%
  # group by is_treated, variable and values
  group_by(is_treated, variable, values) %>%
  # compute the number of observations
  summarise(n = n()) %>%
  # compute the proportion
  mutate(freq = round(n / sum(n)*100, 0)) %>%
  ungroup() %>%
  filter(!(variable %in% c("rainfall_height_dummy", "rainfall_height_dummy_lag_1") & values == "False")) %>%
  mutate(new_variable = NA %>%
           ifelse(str_detect(variable, "wind"), "Wind Direction",.) %>%
           ifelse(str_detect(variable, "rainfall"), "Rainfall Dummy",.)) %>%
  mutate(time = "\nin t" %>%
           ifelse(str_detect(variable, "lag_1"), "\nin t-1", .)) %>%
  mutate(variable = paste(new_variable, time, sep = " ")) %>%
  mutate(is_treated = if_else(is_treated==TRUE, "Treated", "Control"))


# build the graph for wind direction
graph_categorical_wd_weather <- data_weather_categorical %>%
  filter(new_variable == "Wind Direction") %>%
  ggplot(., aes(x = freq, y = values, fill = is_treated)) +
  geom_point(shape = 21, size = 6, alpha = 0.8) +
  scale_fill_manual(values = c("deepskyblue3", "coral")) +
  facet_wrap(~ variable, scales = "free") +
  ylab("Proportion (%)") +
  xlab("") + 
  labs(fill = "Units Status:") +
  custom_theme +
  theme(legend.position = "top", legend.justification = "left", legend.direction = "horizontal")

# we print the graph
graph_categorical_wd_weather

# build the graph for rainfall dummy
graph_categorical_rainfall_weather <- data_weather_categorical %>%
  filter(new_variable == "Rainfall Dummy") %>%
  ggplot(., aes(x = freq, y = variable, fill = is_treated)) +
  geom_point(shape = 21, size = 6, alpha = 0.8) +
  scale_fill_manual(values = c("deepskyblue3", "coral")) +
  ylab("Proportion (%)") +
  xlab("") + 
  labs(fill = "Units Status:") +
  custom_theme +
  theme(legend.position = "top", legend.justification = "left", legend.direction = "horizontal")

# we print the graph
graph_categorical_rainfall_weather

# combine plots
graph_categorical_weather <- graph_categorical_wd_weather / graph_categorical_rainfall_weather +
  plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(size = 30, face = "bold"))

# save the graph
ggsave(graph_categorical_weather, filename = here::here("3.outputs", "1.figures", "2.analysis_pollution", "1.cruise_experiment", "1.checking_matching_procedure", "graph_categorical_weather.pdf"), 
       width = 60, height = 40, units = "cm", device = cairo_pdf)
````

### Pollutants

For pollutants lag 1, we draw boxplots for treated and control groups:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=28, fig.height=18, dev = "CairoPNG"}
# we select control variables and store them in a long dataframe
data_pollutant_variables <- data_matched %>%
  dplyr::select(mean_no2_l_lag_1:mean_o3_l_lag_1,
         is_treated) %>%
  # transform the data to long to compute the proportion of observations for each variable
  pivot_longer(cols = -c(is_treated), names_to = "variable", values_to = "values") %>%
  mutate(is_treated = ifelse(is_treated=="TRUE", "Treated", "Control")) %>%
  mutate(pollutant = NA %>%
           ifelse(str_detect(variable, "no2_l"), "NO2 Longchamp",.) %>%
           ifelse(str_detect(variable, "no2_sl"), "NO2 Saint-Louis",.) %>%
           ifelse(str_detect(variable, "o3"), "O3 in Longchamp",.) %>%
           ifelse(str_detect(variable, "pm10_l"), "PM10 Longchamp",.) %>%
           ifelse(str_detect(variable, "pm10_sl"), "PM10 Saint-Louis",.) %>%
            ifelse(str_detect(variable, "pm25"), "PM2.5 Longchamp",.) %>%
           ifelse(str_detect(variable, "so2"), "SO2 Longchamp",.)) %>%
  mutate(time = "\nin t-1") %>%
  mutate(variable = paste(pollutant, time, sep = " "))

# make graph
graph_boxplot_pollutants <- data_pollutant_variables %>%
  ggplot(., aes(x = is_treated, y = values, colour = is_treated)) + 
  geom_violin(size = 2) + 
  geom_boxplot(width=0.1, outlier.shape=NA) +
  scale_color_manual(values=c("deepskyblue3", "coral")) +
  ylab("Concentration (µg/m³)") +
  xlab("") + 
  labs(colour = "Units Status:") +
  facet_wrap(~variable, scale = "free", ncol = 4) +
  custom_theme +
  theme(legend.position = "top", legend.justification = "left", legend.direction = "horizontal")

# we print the graph
graph_boxplot_pollutants

# save the graph
ggsave(graph_boxplot_pollutants, filename = here::here("3.outputs", "1.figures", "2.analysis_pollution", "1.cruise_experiment", "1.checking_matching_procedure", "graph_boxplot_pollutants.pdf"), 
       width = 80, height = 50, units = "cm", device = cairo_pdf)
````

### Road Traffic

For road traffic flow, we draw boxplots for treated and control groups over the 0-2 lags:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=28, fig.height=18, dev = "CairoPNG"}
# we select control variables and store them in a long dataframe
data_road_traffic_variables <- data_matched %>%
  dplyr::select(road_traffic_flow_all, road_traffic_flow_trucks_lag_1,road_traffic_flow_trucks, road_traffic_flow_all_lag_1,road_occupancy_rate,road_occupancy_rate_lag_1,
         is_treated) %>%
  rename("Road Traffic Flow in t" = road_traffic_flow_all, "Road Traffic Flow in t-1" = road_traffic_flow_all_lag_1, "Road Traffic Flow >=9m in t"=road_traffic_flow_trucks, "Road Traffic Flow >=9m in t-1"=road_traffic_flow_trucks_lag_1,"Road Occupancy rate in t"=road_occupancy_rate,"Road Occupancy rate in t-1"=road_occupancy_rate_lag_1) %>%
  # transform the data to long to compute the proportion of observations for each variable
  pivot_longer(cols = -c(is_treated), names_to = "variable", values_to = "values") %>%
  mutate(is_treated = ifelse(is_treated=="TRUE", "Treated", "Control"))

# make graph
graph_boxplot_road_traffic <- data_road_traffic_variables %>%
  ggplot(., aes(x = is_treated, y = values, colour = is_treated)) + 
  geom_violin(size = 2) + 
  geom_boxplot(width=0.1, outlier.shape=NA) +
  scale_color_manual(values=c("deepskyblue3", "coral")) +
  ylab("Covariate Value") +
  xlab("") + 
  labs(colour = "Units Status:") +
  facet_wrap(~variable, scale = "free", ncol = 4) +
  custom_theme +
  theme(legend.position = "top", legend.justification = "left", legend.direction = "horizontal")

# we print the graph
graph_boxplot_road_traffic

# save the graph
ggsave(graph_boxplot_road_traffic, filename = here::here("3.outputs", "1.figures", "2.analysis_pollution", "1.cruise_experiment", "1.checking_matching_procedure", "graph_boxplot_road_traffic.pdf"), 
       width = 40, height = 20, units = "cm", device = cairo_pdf)
````

### Calendar Indicator

For calendar variables such as the day of the week, bank days and holidays we matched strictly. We plot the proportions of observations belonging to each month by treatment status:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=35, fig.height=14, dev = "CairoPNG"}
# compute the proportions of observations belonging to each month by treatment status
data_month <- data_matched %>%
  mutate(is_treated = ifelse(is_treated=="TRUE", "Treated", "Control")) %>%
  dplyr::select(month, is_treated) %>%
  mutate(month = recode(month, `1` = "January",
                               `2` = "February",
                               `3` = "March",
                               `4` = "April",
                               `5` = "May",
                               `6` = "June",
                               `7` = "July",
                               `8` = "August",
                               `9` = "September",
                               `10` = "October",
                               `11` = "November",
                               `12` = "December") %>%
           fct_relevel(., "January", "February", "March","April", "May", "June", "July", "August", "September", "October", "November", "December")) %>%
  pivot_longer(., -is_treated) %>%
  group_by(name, is_treated, value) %>%
  summarise(n = n()) %>%
  mutate(proportion = round(n / sum(n)*100,0)) %>%
  ungroup()

# we plot the data using cleveland dot plots
graph_month <- ggplot(data_month, aes(x = as.factor(value), y = proportion, colour = is_treated, group = is_treated)) +
  geom_line(size = 2) +
  scale_colour_manual(values=c("deepskyblue3", "coral"), guide = guide_legend(reverse = FALSE)) +
  expand_limits(x = 0, y = 0) +
  ggtitle("Month") +
  ylab("Proportion (%)") +
  xlab("") + 
  labs(colour = "Units Status:") +
  custom_theme +
  theme(legend.position = "top", legend.justification = "left", legend.direction = "horizontal")

# we print the graph
graph_month
````

We plot the proportions of observations belonging to each year by treatment status:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=30, fig.height=14, dev = "CairoPNG"}
# compute the proportions of observations belonging to each year by treatment status
data_year <- data_matched %>%
  mutate(is_treated = ifelse(is_treated=="TRUE", "Treated", "Control")) %>%
  dplyr::select(
         year, is_treated) %>%
  pivot_longer(., -is_treated) %>%
  group_by(name, is_treated, value) %>%
  summarise(n = n()) %>%
  mutate(proportion = round(n / sum(n)*100,0)) %>%
  ungroup()

# we plot the data using cleveland dot plots
graph_year <- ggplot(data_year, aes(x = as.factor(value), y = proportion, colour = is_treated, group = is_treated)) +
  geom_line(size = 2) +
  scale_colour_manual(values=c("deepskyblue3", "coral"), guide = guide_legend(reverse = FALSE)) +
  expand_limits(x = 0, y = 0) +
  ggtitle("Year") +
  ylab("Proportion (%)") +
  xlab("") + 
  labs(colour = "Units Status:") +
  custom_theme +
  theme(legend.position = "top", legend.justification = "left", legend.direction = "horizontal")

# we print the graph
graph_year
````

We combine and save the two previous plots:

```{R, echo=TRUE, message = FALSE, warning = FALSE, layout="l-body-outset", fig.width=28, fig.height=18, dev = "CairoPNG"}
# combine plots
graph_month_year <- graph_month / graph_year +
  plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(size = 30, face = "bold"))

# save the plot
ggsave(graph_month_year, filename = here::here("3.outputs", "1.figures", "2.analysis_pollution", "1.cruise_experiment", "1.checking_matching_procedure", "graph_month_year.pdf"), 
       width = 40, height = 40, units = "cm", device = cairo_pdf)
````




