---
title: "Figures for the Article"
description: |
  Detailed Script.
author:
  - name: Marie-Abèle Bind 
    url: https://scholar.harvard.edu/marie-abele
    affiliation: Harvard University
    affiliation_url: https://statistics.fas.harvard.edu/people/marie-abale-bind
  - name: Marion Leroutier 
    url: https://www.parisschoolofeconomics.eu/en/leroutier-marion/work-in-progress/
    affiliation: Paris School of Economics
    affiliation_url: https://www.parisschoolofeconomics.eu/en/
  - name: Léo Zabrocki 
    url: https://www.parisschoolofeconomics.eu/en/
    affiliation: Paris School of Economics
    affiliation_url: https://www.parisschoolofeconomics.eu/en/
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
      toc: true
      toc_depth: 3
---

<style>
body {
text-align: justify}
</style>

In this document, we provide all steps and R codes required to reproduce the figure displayed in the main article for the daily analysis.

**Should you have any questions, need help to reproduce the analysis or find coding errors, please do not hesitate to contact us at leo.zabrocki@psemail.eu and marion.leroutier@psemail.eu.**

# Required Packages

To reproduce exactly the `script_figures_paper.html` document, we first need to have installed:

* the [R](https://www.r-project.org/) programming language 
* [RStudio](https://rstudio.com/), an integrated development environment for R, which will allow you to knit the `5_script_checking_balance_figures.Rmd` file and interact with the R code chunks
* the [R Markdown](https://rmarkdown.rstudio.com/) package
* and the [Distill](https://rstudio.github.io/distill/) package which provides the template for this document. 

Once everything is set up, we have to load the following packages:

```{r, echo = TRUE, message = FALSE, warning = FALSE}
# load required packages
library(knitr) # for creating the R Markdown document
library(here) # for files paths organization
library(tidyverse) # for data manipulation and visualization
library(Cairo) # for printing customed police of graphs
```

We finally load our customed `ggplot2` theme for graphs:

```{r, echo = TRUE, message = FALSE, warning = FALSE}
# load ggplot customed theme
source(here::here("2.scripts", "5.custom_ggplot2_theme", "script_custom_ggplot_theme.R"))
````

The theme is based on the fantastic [hrbrthemes](https://hrbrmstr.github.io/hrbrthemes/index.html) package. If you do not want to use this theme or are unable to install it because of fonts issues, you can use the `theme_bw()` already included in the `ggplot2` package.

# Preparing the Data

We load the data on 95% Fisherian intervals:

```{R, echo = TRUE}
# load fisherian intervals data
data <-
  readRDS(
    here::here(
      "1.data",
      "2.data_for_analysis",
      "6.submission_natcomms",
      "ri_data_fisherian_intervals.rds"
    )
  )
```


For clarity, we only display in the main paper the results for NO$_{2}$, SO$_{2}$, PM$_{10}$ and PM$_{2.5}$ over the -1 to +1 days period.

```{R, echo = TRUE}
data <- data %>%
  filter(!str_detect(pollutant, "O3"))
```


# Graph of 95% Fisherian Intervals

We plot below the results of our randomization inference to compute 95% Fisherian intervals:

```{R, echo=TRUE, layout="l-body-outset", fig.width=20, fig.height=10, warning = FALSE, dev = "CairoPNG"}
data <- data %>%
  mutate(pollutant = ifelse(str_detect(pollutant, "SO2"), "SO2 Longchamp", pollutant)) %>%
  arrange(pollutant, time) %>%
  mutate(stripe = ifelse((time %% 2) == 0, "Grey", "White")) %>%
  ungroup()






# make the graph
graph_fi <- ggplot(data, aes(x = as.factor(time), y = observed_mean_difference, ymin = lower_fi,
                        ymax = upper_fi)) +
  geom_rect(aes(fill = stripe), xmin = as.numeric(as.factor(data$time))-0.42,
            xmax = as.numeric(as.factor(data$time))+0.42, ymin = -Inf, ymax=Inf, color = NA, alpha = 0.4) +
          scale_fill_manual(values = c('gray96', NA)) +
  geom_hline(yintercept = 0, color="black") +
  geom_vline(xintercept = c(1.6), color = "black") +
  geom_pointrange(aes(x = as.factor(time), y = observed_mean_difference, ymin = lower_fi ,
                      ymax = upper_fi), colour="deepskyblue3", lwd = 1.2) +
  facet_wrap(~ factor(
    pollutant,
    levels = c(
      "NO2 Saint-Louis",
      "NO2 Longchamp",
      "SO2 Longchamp",
      "PM10 Saint-Louis",
      "PM10 Longchamp",
      "PM2.5 Longchamp")
    )) +
  labs(colour = "Vessel Traffic:") +
  ylab("Constant-Additive Increase \nin Concentrations (µg/m³)") + xlab("Day") +
  custom_theme +
  guides(fill = FALSE) +
  theme(legend.position = "top", legend.justification = "left", legend.direction = "horizontal")

# print the graph
graph_fi

# save the graph
ggsave(graph_fi, filename = here::here("3.outputs", "1.figures", "3.figures_paper", "graph_fisherian_intervals_article.pdf"), width = 40, height = 20, units = "cm", device = cairo_pdf)
```
